### 2023-06-12 visit_scotland_notebook.Rmd
Project Structure Setup & Initial Analysis

---
title: "Visit Scotland Notebook"
output: html_notebook
---

## Load Libraries

```{r}
library(tidyverse)
library(here)
```

## Run Cleaning Script

```{r}
source(here("scripts/cleaning_script.R"))
```

## Read In Clean Data

```{r}

demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))

```

## Temporal Analysis

### Total Visits Over Time

```{r}

# Total Visits Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = visits, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = visits_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "No. of Visits (Million) \n",
       title = "Number of Visits Over Time") +
  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
```

### Total Expenditure Over Time

```{r}

# Total Expenditure Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = expenditure, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_change_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Million) \n",
       title = "Expenditure Over Time") +
  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

```
### Expenditure Per Visit Over Time

```{r}

# Expenditure Per Visit Over Time

demographics_all %>% 
  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
  geom_line(size = 1, colour = "grey") +
  geom_point(aes(colour = exp_per_visit_label), 
             show.legend = FALSE,
             size = 4) +
  labs(x = "\n Year",
       y = "Expenditure (Millions) per Visit (Millions) \n",
       title = "Expenditure To Visit Ratio \n") +
  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))

```

## Demographic Analysis

- Highest Mean Spend Per Visit (2013-2018) vs. 2019
- Highest Mean Spend Per Visit.

### Age

Spend Per Visit Over Period: 45-54
Spend Per Visit (2013-2018) vs. 2019: 
- Increase in 25-34, 35-44, 55-64, 65+
- Interesting decrease in 45-54 despite being highest mean across all years.

Conclusion: May suggest that there is scope for growth in other age groups, but not in 45-54.

```{r}
age_demographics %>%
  group_by(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Age Group")
```

```{r}

age_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(age, is_2019) %>%
  arrange(age) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = age, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Age",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Age Group")

```

### Gender

Highest Mean Spend Per Visit Over Period: Little difference between male and female spend per visit.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Little difference between genders, both show potential for growth.

```{r}
gender_demographics %>%
  group_by(gender) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Gender")
```

```{r}
gender_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(gender, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = gender, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Gender",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Gender")
```

### Marital Status

Highest Mean Spend Per Visit Over Period: Married people spend more than un-married.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although married people were already spending the most per visit, their spend increased by a larger amount in 2019 than un-married people, suggesting there is still plenty of room for growth.

```{r}
marital_demographics %>%
  group_by(marital_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = marital_status, y = mean_exp_per_visit, fill = marital_status == "Married"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Marital Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Marital Status")
```

```{r}
marital_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(marital_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = marital_status, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Marital Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Marital Status")
```

### Children

Highest Mean Spend Per Visit Over Period: People with children spent more per visit than people without.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although people with children spend more per visit than people without, both categories increased spending per visit in 2019 suggesting there is room for growth in both areas.

```{r}
children_demographics %>%
  group_by(children) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = children, y = mean_exp_per_visit, fill = children == "Yes - Children"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Children",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Children")
```

```{r}
children_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(children, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = children, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Children",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Children")
```

### Employment

Highest Mean Spend Per Visit Over Period: People in employment have the highest average spend per visit.
Mean Spend Per Visit (2013-2018) vs. 2019: All Increased.

Conclusion: Although people in employment have the highest spend per visit there was rleatively little growth in this area in 2019. By comparison both other categories increase their spend per visit suggesting theire is potential for growth in these areas.

```{r}
employment_demographics %>%
  group_by(employment_status) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Employment",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Employment")
```

```{r}
employment_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(employment_status, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = employment_status, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Employment Status",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Employment Status")
```

### Car Access

Highest Mean Spend Per Visit Over Period: People with access to a car spent more per visit on average.
Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.

Conclusion: Although people with access to a car spend more per visit, spend per visit amongst those without access to a car increased by more than those with a car. Highlights potential growth in this areas and particuarly related to transport.

```{r}
car_demographics %>%
  group_by(access_to_car) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Car Access",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Car Access")
```
```{r}
car_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(access_to_car, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = access_to_car, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Access To Car",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Access To Car")
```

### Social Grade

AB	Higher & intermediate managerial, administrative, professional occupations.
C1	Supervisory, clerical & junior managerial, administrative, professional occupations.
C2	Skilled manual occupations.
DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations.

```{r}
social_demographics %>%
  group_by(social_grade) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  ggplot() +
  geom_col(aes(x = social_grade, y = mean_exp_per_visit, fill = social_grade == "AB"),
           show.legend = FALSE) +
  scale_fill_manual(values = c("FALSE" = "grey40",
                               "TRUE" = "forestgreen")) +
  labs(
    x = "\n Social Gradee",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit 2013-2019",
    subtitle = "By Social Grade")
```

```{r}
social_demographics %>% 
  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
  group_by(social_grade, is_2019) %>%
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
  ggplot(aes(x = social_grade, y = difference_exp_per_visit)) +
  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
  scale_fill_manual(values = c("Increased" = "forestgreen",
                               "Decreased" = "firebrick")) +
  labs(
    x = "\n Social Grade",
    y = "Mean Expenditure per Visit \n",
    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
    subtitle = "By Social Grade")
```

## Domestic & International Visitors

### Domestic vs. International

```{r}
domestic_2017_2019_visits <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(visits)

international_2017_2019_visits <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits)) %>% 
  select(total_visits)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$total_visits)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Visits \n",
    title = "Domestic vs. International Visits",
    subtitle = "2017-2019")
```

```{r}
domestic_2017_2019 <- regional_domestic_tourism %>% 
  filter(date_code == "2017-2019",
         region_of_residence == "All of GB") %>% 
  select(expenditure)

international_2017_2019 <- international_visits %>%
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2017, 2018, 2019)) %>% 
  summarise(total_visits = sum(visits),
            total_spend = sum(spend),
            exp_per_visit = total_spend / total_visits) %>% 
  select(total_spend)

tibble(a = c("Domestic", "International"),
       b = c(domestic_2017_2019$expenditure, international_2017_2019$total_spend)) %>% 
  ggplot() +
  geom_col(aes(x = a, y = b)) +
  labs(
    x = "",
    y = "Expenditure \n",
    title = "Domestic vs. International Expenditure",
    subtitle = "2017-2019")
```
### International

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(country %in% c("USA", "Germany", "Australia", "France", "China"),
         year %in% c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) %>% 
  group_by(year, country) %>% 
  summarise(total_spend = sum(spend)) %>% 
  ggplot(aes(x = year, y = total_spend, colour = country)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) +
  labs(x = "\n Year",
       y = "Expenditure (Million) \n",
       title = "Expenditure by Country",
       subtitle = "Top 5 Countries per Total Expenditure")
```

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(country %in% c("USA", "Germany", "France", "Netherlands", "Australia"),
         year %in% c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) %>% 
  group_by(year, country) %>% 
  summarise(total_visits = sum(visits)) %>% 
  ggplot(aes(x = year, y = total_visits, colour = country)) +
  geom_line() +
  geom_point() +
  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
                                2018, 2019)) +
  labs(x = "\n Year",
       y = "Visits (Million) \n",
       title = "Visits by Country",
       subtitle = "Top 5 Countries per Visits")
```

### Domestic

### 2023-06-12 scripts/cleaning_script.R

@@ -1,0 +1,192 @@
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(janitor)
+library(here)
+library(readxl)
+
+# Read In Raw Data ------------------------------------------------------------
+
+demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
+  clean_names()
+
+regional_domestic_tourism <- read_csv("data/raw_data/regional_domestic_tourism.csv") %>%
+  clean_names()
+
+international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
+  clean_names()
+
+# domestic_day_visits <- read_excel("data/raw_data/gbdvs-2019-scotland-and-gb.xlsx") %>% 
+#   clean_names()
+#
+
+# activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>% 
+#   clean_names()
+
+# location <- read_csv("data/raw_data/tourism_day_visits_location.csv") %>% 
+#   clean_names()
+# 
+# transport <- read_csv("data/raw_data/tourism_day_visits_transport.csv") %>% 
+#   clean_names()
+# 
+# accomodation_occupancy <- read_csv("data/raw_data/scottish_accomodation_occupancy.csv") %>% 
+#   clean_names()
+# 
+
+
+# Clean Demographic Data ------------------------------------------------------------
+
+all_demographics_clean <- demographics %>%
+  filter(age == "All", marital_status == "All", gender == "All", employment_status == "All",
+         children == "All",  access_to_car == "All", social_grade == "All") %>%
+  select(-c(measurement, units)) %>% 
+  pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+  arrange(date_code) %>% 
+  mutate(exp_per_visit = Expenditure / Visits,
+         exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
+         visits_change_label = case_when(Visits > lag(Visits) ~ "Increased",
+                                         Visits < lag(Visits) ~ "Decreased",
+                                         Visits == lag(Visits) ~ "No Change",
+                                         TRUE ~ "Starting Year"),
+         exp_change_label = case_when(Expenditure > lag(Expenditure) ~ "Increased",
+                                      Expenditure < lag(Expenditure) ~ "Decreased",
[…]

### 2023-06-12 visit_scotland_notebook.Rmd
Started Domestic vs. International Analysis

@@
 library(here)
+library(modelr)
 ```
@@
 ```{r}
-domestic_2017_2019 <- regional_domestic_tourism %>% 
+domestic_2017_2019_spend <- regional_domestic_tourism %>% 
   filter(date_code == "2017-2019",
@@
 
-international_2017_2019 <- international_visits %>%
+international_2017_2019_spend <- international_visits %>%
   select(-c(quarter, age, sample)) %>%
@@
 tibble(a = c("Domestic", "International"),
-       b = c(domestic_2017_2019$expenditure, international_2017_2019$total_spend)) %>% 
+       b = c(domestic_2017_2019_spend$expenditure, international_2017_2019_spend$total_spend)) %>% 
   ggplot() +
@@
 ```
+
+```{r}
+ips_2002_2019 %>%
+  add_predictions(model) %>%
+  add_residuals(model) %>% 
+  ggplot(aes(x = visits, y = spend)) +
+  geom_point() +
+  geom_line(aes(y = pred), col = "red") +
+  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
+  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
+  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3") +
+  annotate("text", x = 1800, y = 1900, label = "Standard Error: 0.08115")
+```
+
+Diagnostic Plots: Ok, not great but passable.
+
+- R-squared: The proportion of variance explained by the predictor(s).
+
+- p-value: Statistical significance of effect.
+
+- Residual Standard Error: Average distance that the observed values fall from the regression line. The smaller the value, the better the regression model is able to fit the data.
+
+- Standard error: Uncertainty around estimated coefficient.
+
 ### International
@@
 
+### USA
+
 ### Domestic

### 2023-06-12 scripts/cleaning_script.R

@@ -158,9 +158,18 @@ regional_domestic_tourism_clean <- regional_domestic_tourism %>%
   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
   clean_names()
 
-# Clean International Domestic Tourism Data (Overnights) ------------------------------------------------------------
+# Create International Passenger Survey Tibble  ------------------------------------------------------------
 
+## Raw data available 'regional_spread_by_year_2002_-_2021_pivot.xlsx'. Heavily formatted .xlsx.
 
+ips_2002_2019 <- tibble(year = c(2002,	2003,	2004,	2005,	2006,	2007,	2008,	2009,	2010,	2011,	
+                                 2012,	2013,	2014,	2015,	2016,	2017,	2018,	2019),
+                        visits = c(1581, 1565,	1881,	2392,	2732,	2791,	2492,	2564,	2319,	2367,	
+                                   2249,	2436,	2690,	2635,	2871,	3432,	3729,	3460),
+                        spend = c(806, 837, 994, 1208, 1439, 1367, 1241, 1397, 1422, 1478, 1398, 
+                                  1671, 1868, 1720, 1944, 2459, 2379, 2538),
+                        nights = c(15040, 14949,	19006, 24330,	26376, 24541, 19524, 21980, 21176,	17704, 
+                                   17645, 19441, 21940, 21443,	22483, 26451,	25443, 27385))
 
 # Write Clean Data To .CSV -----------------------------------------------------------
 

### 2023-06-12 draft_work.Rmd
Added "Draft" Notebook

---
title: "R Notebook"
output: html_notebook
---

```{r}
international_visits %>%
  group_by(year, quarter, country) %>%
  summarise(total_visits = sum(visits),
            total_spend = sum(spend)) %>% 
  ggplot(aes(x = total_visits, y = total_spend)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}
demographics_all %>% 
  ggplot(aes(x = visits, y = expenditure)) +
  geom_point() +
  geom_smooth(method = "lm")
```

```{r}

ips_2002_2019 %>% 
  ggplot(aes(x = visits, y = spend)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    x = "Visits (Million)",
    y = "Expenditure (£Million) \n",
    title = "Scotland: International Visits vs. Spend",
    subtitle = "2012-2019")

```

```{r}

model <- lm(formula = spend ~ visits, data = ips_2002_2019)

model2 <- lm(formula = spend ~ visits + nights, data = ips_2002_2019)

```

```{r}
summary(model)
```

```{r}
summary(model2)
```

```{r}
library(modelr)
```

```{r}

ips_2002_2019 %>%
  add_predictions(model) %>%
  add_residuals(model) %>% 
  ggplot(aes(x = visits, y = spend)) +
  geom_point() +
  geom_line(aes(y = pred), col = "red") +
  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3")

```

```{r}
library(ggfortify)
```

```{r}
autoplot(model)
```

### 2023-06-13 draft_work.Rmd
Re-plotted Demographic Plots Based On %, Added International Models

@@
 ```{r}
-international_visits %>%
-  group_by(year, quarter, country) %>%
-  summarise(total_visits = sum(visits),
-            total_spend = sum(spend)) %>% 
-  ggplot(aes(x = total_visits, y = total_spend)) +
-  geom_point() +
-  geom_smooth(method = "lm")
+library(broom)
+library(factoextra)
 ```
@@
 ```{r}
-demographics_all %>% 
-  ggplot(aes(x = visits, y = expenditure)) +
-  geom_point() +
-  geom_smooth(method = "lm")
+activities %>%
+  group_by(tourism_activity) %>%
+  mutate(exp_per_visit = Expenditure / Visits) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
+               fill = tourism_activity == "Shopping for items that you do not regularly buy"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Expenditure \n",
+    title = "Mean Expenditure per Activity  2013-2019") +
+  coord_flip()
+  # theme(axis.text.x = element_text(angle = 45, hjust=1))
 ```
@@
 ```{r}
+activities %>% 
+  mutate(is_2019 = if_else(date_code == 2019, "2019", "2013-2018")) %>% 
+  group_by(tourism_activity, is_2019) %>%
+  arrange(tourism_activity) %>% 
+  mutate(exp_per_visit = Expenditure / Visits) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit), y = difference_exp_per_visit)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
+  coord_flip()
+```
 
-ips_2002_2019 %>% 
-  ggplot(aes(x = visits, y = spend)) + 
-  geom_point() +
-  geom_smooth(method = "lm", se = FALSE) +
-  labs(
-    x = "Visits (Million)",
-    y = "Expenditure (£Million) \n",
-    title = "Scotland: International Visits vs. Spend",
-    subtitle = "2012-2019")
+-----------
 
+```{r}
+activities_summary <- activities %>%
+  group_by(tourism_activity) %>% 
+  summarise(mean_expenditure = mean(Expenditure),
+            mean_visits = mean(Visits),
+            exp_per_visit = mean_expenditure / mean_visits) %>% 
+  arrange(desc(exp_per_visit))
 ```
@@
 ```{r}
-
-model <- lm(formula = spend ~ visits, data = ips_2002_2019)
-
-model2 <- lm(formula = spend ~ visits + nights, data = ips_2002_2019)
-
+activities_clust <- activities %>%
+  group_by(tourism_activity) %>% 
+  summarise(total_expenditure = sum(Expenditure),
+            total_visits = sum(Visits)) %>% 
+  select(total_expenditure, total_visits)
 ```
@@
 ```{r}
-summary(model)
+min_k <- 1
+max_k <- 5
+
+k_clusters <- tibble(k = min_k:max_k) %>% 
+  mutate(kclust = map(k, ~ kmeans(activities_clust, # Create K-means cluster beteen 1-25 clusters.
+                                  centers = .x,
+                                  nstart = 25)),
+         tidied = map(kclust, tidy), # Tidies `kclust`
+         glanced = map(kclust, glance), # Uses tidied to create a glance
+         augmented = map(kclust, augment, activities_summary)) # Adds labels
+
+# Unnest `glanced` to view `tot.withinss`
+clusterings <- k_clusters %>% 
+  unnest(glanced)
+
+clusterings
 ```
@@
 ```{r}
-summary(model2)
+clusterings %>% 
+  ggplot(aes(x = k, y = tot.withinss)) +
+  geom_point() +
+  geom_line() +
+  scale_x_continuous(breaks = seq(1, 25, 1))
 ```
@@
 ```{r}
-library(modelr)
+fviz_nbclust(activities_clust,
+             kmeans,
+             method = "wss", #within sum of squares
+             nstart = 25)
 ```
@@
 ```{r}
-
-ips_2002_2019 %>%
-  add_predictions(model) %>%
-  add_residuals(model) %>% 
-  ggplot(aes(x = visits, y = spend)) +
-  geom_point() +
-  geom_line(aes(y = pred), col = "red") +
-  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
-  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
-  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3")
-
+fviz_nbclust(activities_clust,
+             kmeans,
+             method = "silhouette",
+             nstart = 25)
 ```
@@
 ```{r}
-library(ggfortify)
+clusterings %>% 
+  unnest(augmented) %>% # Unnest augmented created in step 5.1
+  filter(k == 2) %>% # Set number of clusters
+  ggplot(aes(x = total_visits, y = total_expenditure, colour = .cluster)) +
+  geom_point()
 ```
@@
 ```{r}
-autoplot(model)
+clusterings %>% 
+  unnest(augmented) %>% # Unnest augmented created in step 5.1
+  filter(k == 2) %>% 
+  group_by(.cluster)
 ```
+
+-----------------------------------------------------------

### 2023-06-13 visit_scotland_notebook.Rmd
Re-plotted Demographic Plots Based On %, Added International Models

@@
 library(modelr)
+library(ggfortify)
 ```
@@
 regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
+activities <- read_csv(here("data/clean_data/activities_clean.csv"))
 
@@
   ggplot() +
-  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
+  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
            show.legend = FALSE) +
@@
     title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Age Group")
+    subtitle = "By Age Group") +
+  coord_flip()
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = age, y = difference_exp_per_visit)) +
+  ggplot(aes(x = reorder(age, difference_exp_per_visit), y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Age",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Age Group")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 
@@
     y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Gender")
+    title = "Mean Expenditure per Visit 2013-2019")
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = gender, y = difference_exp_per_visit)) +
+  ggplot(aes(x = gender, y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Gender",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Gender")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = marital_status, y = difference_exp_per_visit)) +
+  ggplot(aes(x = marital_status, y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Marital Status",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Marital Status")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = children, y = difference_exp_per_visit)) +
+  ggplot(aes(x = children, y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Children",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Children")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = employment_status, y = difference_exp_per_visit)) +
+  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Employment Status",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Employment Status")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = access_to_car, y = difference_exp_per_visit)) +
+  ggplot(aes(x = access_to_car, y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Access To Car",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Access To Car")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 ```
@@
   ggplot() +
-  geom_col(aes(x = social_grade, y = mean_exp_per_visit, fill = social_grade == "AB"),
+  geom_col(aes(x = reorder(social_grade, mean_exp_per_visit), y = mean_exp_per_visit, fill = social_grade == "AB"),
            show.legend = FALSE) +
@@
     y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Social Grade")
+    title = "Mean Expenditure per Visit 2013-2019") +
+  coord_flip()
 ```
@@
   filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = social_grade, y = difference_exp_per_visit)) +
+  ggplot(aes(x = reorder(social_grade, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
   geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
   scale_fill_manual(values = c("Increased" = "forestgreen",
@@
     x = "\n Social Grade",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018",
-    subtitle = "By Social Grade")
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
 ```
@@
 
+### International
+
+#### Summary
+
 ```{r}
 ips_2002_2019 %>%
-  add_predictions(model) %>%
-  add_residuals(model) %>% 
+  summarise(cor(spend, visits))
+```
+
+```{r}
+model_ips <- lm(formula = spend ~ visits, data = ips_2002_2019)
+summary(model_ips)
+```
+
+```{r}
+autoplot(model_ips)
+```
+
+```{r}
+ips_2002_2019 %>%
+  add_predictions(model_ips) %>%
+  add_residuals(model_ips) %>% 
   ggplot(aes(x = visits, y = spend)) +
@@
   annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
-  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 4.78e-06") +
-  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.8876 / Residual Standard Error: 183.3") +
-  annotate("text", x = 1800, y = 1900, label = "Standard Error: 0.08115")
+  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 2.46e-08") +
+  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.864 / Residual Standard Error: 195.2") +
+  labs(
+    x = "Visits (Million)",
+    y = "Expenditure (£Million) \n",
+    title = "Scotland: International Visits vs. Spend",
+    subtitle = "2002-2019")
 ```
 
-Diagnostic Plots: Ok, not great but passable.
-
-- R-squared: The proportion of variance explained by the predictor(s).
-
-- p-value: Statistical significance of effect.
-
-- Residual Standard Error: Average distance that the observed values fall from the regression line. The smaller the value, the better the regression model is able to fit the data.
-
-- Standard error: Uncertainty around estimated coefficient.
-
-### International
+#### By Country
 
@@
 
-### USA
+#### USA
+
+```{r}
+ips_2002_2019_usa %>%
+  summarise(cor(spend, visits))
+```
+
+```{r}
+model_ips_usa <- lm(formula = spend ~ visits, data = ips_2002_2019_usa)
+summary(model_ips_usa)
+```
+
+Model: spend ~ visits
+
+Interpretation: ~83% of the variation in expenditure can be explained by the number of visits.
+
+Question: USA visits increased by 11.5789% between 2018 and 2019 to 636 Million. If this percentage increase in visits was replicated in 2020 (709.642m), what would our model predict for expenditure?
+
+Answer: If USA visits were increased as above, the model would predict expenditure of ~£723m (Low Estimate ~£655m, High Estimate ~£791m)
+
+As calculated below.
+
+Step 1.
+outcome = b0 + b1 * 1st Predictor
+
+Step 2.
+expenditure = b0(intercept) + b1(coefficient) * 1st Predictor
+
+Step 3.
+expenditure = b0(intercept) + b1(coefficient) * `visits`
+
+Step 4.
+expenditure = -195.9631 + 1.2953 * `709.642`
+
+Step 5.
+expenditure = 723.2287 (Low Estimate 655.3287, High Estimate 791.1287)
+
+```{r}
+
+predict_at <- data.frame(visits = c(709.642))
+
+# get predicted heights at those sample_weights
+predict(model_ips_usa, newdata = predict_at)
+```
+
+```{r}
+723.2287  + c(-67.9, 67.9)
+```
+
+```{r}
+ips_2002_2019_usa %>%
+  add_predictions(model_ips_usa) %>%
+  add_residuals(model_ips_usa) %>% 
+  ggplot(aes(x = visits, y = spend)) +
+  geom_point() +
+  geom_line(aes(y = pred), col = "red") +
+  labs(
+    x = "Visits (Million)",
+    y = "Expenditure (£Million) \n",
+    title = "Scotland: USA Visits vs. Spend",
+    subtitle = "2002-2019")
+```
+
+```{r}
+autoplot(model_ips_usa)
+```
 

### 2023-06-13 scripts/cleaning_script.R

@@ -17,11 +17,10 @@ regional_domestic_tourism <- read_csv("data/raw_data/regional_domestic_tourism.c
 international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
   clean_names()
 
-# domestic_day_visits <- read_excel("data/raw_data/gbdvs-2019-scotland-and-gb.xlsx") %>% 
-#   clean_names()
-#
+activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
+  clean_names()
 
-# activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>% 
+# domestic_day_visits <- read_excel("data/raw_data/gbdvs-2019-scotland-and-gb.xlsx") %>% 
 #   clean_names()
 
 # location <- read_csv("data/raw_data/tourism_day_visits_location.csv") %>% 
@@ -139,16 +138,6 @@ social_demographics_clean <- demographics %>%
   rename(year = date_code) %>% 
   clean_names()
 
-
-# Clean Domestic Day Visit Data ------------------------------------------------------------
-
-# domestic_day_visits_clean <- domestic_day_visits %>% 
-#   filter(regions == "Scotland") %>% 
-#   mutate(toursism_exp_per_visit = tourism_day_visit_spend_m / tourism_day_visits_m,
-#          toursism_exp_per_visit_pct_change = (toursism_exp_per_visit - lag(toursism_exp_per_visit)) / lag(toursism_exp_per_visit) * 100,
-#          leisure_exp_per_visit = leisure_day_visits_spend_m / leisure_day_visits_m,
-#          leisure_exp_per_visit_pct_change = (leisure_exp_per_visit - lag(leisure_exp_per_visit)) / lag(leisure_exp_per_visit) * 100)
-
 # Clean Regional Domestic Tourism Data (Overnights) ------------------------------------------------------------
 
 regional_domestic_tourism_clean <- regional_domestic_tourism %>%
@@ -171,6 +160,24 @@ ips_2002_2019 <- tibble(year = c(2002,	2003,	2004,	2005,	2006,	2007,	2008,	2009,
                         nights = c(15040, 14949,	19006, 24330,	26376, 24541, 19524, 21980, 21176,	17704, 
                                    17645, 19441, 21940, 21443,	22483, 26451,	25443, 27385))
 
+ips_2002_2019_usa <- tibble(year = c(2002,	2003,	2004,	2005,	2006,	2007,	2008,	2009,	2010,	2011,	
[…]

### 2023-06-13 draft_work.Rmd
Drafted Basic Activities Plots / Cleaned Additional USA Visitor Data

@@
 library(factoextra)
-```
-
-```{r}
-activities %>%
-  group_by(tourism_activity) %>%
-  mutate(exp_per_visit = Expenditure / Visits) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
-               fill = tourism_activity == "Shopping for items that you do not regularly buy"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Activity",
-    y = "Mean Expenditure \n",
-    title = "Mean Expenditure per Activity  2013-2019") +
-  coord_flip()
-  # theme(axis.text.x = element_text(angle = 45, hjust=1))
-```
-
-```{r}
-activities %>% 
-  mutate(is_2019 = if_else(date_code == 2019, "2019", "2013-2018")) %>% 
-  group_by(tourism_activity, is_2019) %>%
-  arrange(tourism_activity) %>% 
-  mutate(exp_per_visit = Expenditure / Visits) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit), y = difference_exp_per_visit)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Activity",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
-  coord_flip()
 ```

### 2023-06-13 visit_scotland_notebook.Rmd
Drafted Basic Activities Plots / Cleaned Additional USA Visitor Data

@@
 activities <- read_csv(here("data/clean_data/activities_clean.csv"))
+usa_visit_spend_region <- read_csv(here("data/clean_data/usa_visit_spend_region_clean.csv"))
 
@@
   labs(x = "\n Year",
-       y = "Expenditure (Million) \n",
+       y = "Expenditure (Million Pounds, GBP) \n",
        title = "Expenditure Over Time") +
@@
   labs(x = "\n Year",
-       y = "Expenditure (Millions) per Visit (Millions) \n",
-       title = "Expenditure To Visit Ratio \n") +
+       y = "Expenditure (Million Pounds, GBP) per Visit (Millions) \n",
+       title = "Expenditure Per Visit \n") +
   scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
@@
     y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Age Group") +
+    title = "Mean Expenditure per Visit 2013-2019") +
   coord_flip()
@@
 
+## Activities
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
+               fill = tourism_activity == "Shopping for Non-Regular Purchases"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(tourism_activity, is_2019) %>%
+  arrange(tourism_activity) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Activity",
+    y = "% Difference \n",
+    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
 ## Domestic & International Visitors

### 2023-06-13 scripts/cleaning_script.R

@@ -33,7 +33,6 @@ activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
 #   clean_names()
 # 
 
-
 # Clean Demographic Data ------------------------------------------------------------
 
 all_demographics_clean <- demographics %>%
@@ -149,7 +148,7 @@ regional_domestic_tourism_clean <- regional_domestic_tourism %>%
 
 # Create International Passenger Survey Tibble  ------------------------------------------------------------
 
-## Raw data available 'regional_spread_by_year_2002_-_2021_pivot.xlsx'. Heavily formatted .xlsx.
+## Raw data available 'regional_spread_by_year_2002_-_2021_pivot.xlsx'. Pivot Table.
 
 ips_2002_2019 <- tibble(year = c(2002,	2003,	2004,	2005,	2006,	2007,	2008,	2009,	2010,	2011,	
                                  2012,	2013,	2014,	2015,	2016,	2017,	2018,	2019),
@@ -169,13 +168,59 @@ ips_2002_2019_usa <- tibble(year = c(2002,	2003,	2004,	2005,	2006,	2007,	2008,	2
                         nights = c(2919, 3264, 3883, 2717, 4469, 3633, 2759, 2967, 2042, 2460, 
                                    2653, 2172, 3538, 4005, 4420, 5710, 4492, 4246))
 
+# Import USA Spend and Visitor Data Demographic Data ------------------------------------------------------------
+
+## Raw data available 'subregion_trend_by_purpose_country_2009-2021.xlsx'. Pivot Table.
+
+usa_visitors_2009_2019 <- read_csv("data/raw_data/usa_visitors_region.csv") %>% clean_names()
+
+usa_visitors_2009_2019_clean <- usa_visitors_2009_2019 %>% 
+  pivot_longer(
+    cols = c("x2009", "x2010", "x2011", "x2012", "x2013", "x2014", "x2015", "x2016", "x2017", "x2018", "x2019"),
+    names_to = "year",
+    values_to = "visits"
+  ) %>% 
+  mutate(year = str_remove(year, "x"))
+
+usa_spend_2009_2019 <- read_csv("data/raw_data/usa_spend_region.csv") %>% clean_names()
+
+usa_spend_2009_2019_clean <- usa_spend_2009_2019 %>% 
+  pivot_longer(
[…]

### 2023-06-13 draft_work.Rmd
Began Work Adding Leaflet Map For USA Visitors per Region

@@
 library(factoextra)
+library(sf)
+```
+
+```{r}
+usa_visit_spend_region %>%
+  group_by(region) %>% 
+  summarise(mean_spend = mean(spend),
+            mean_visits = mean(visits)) %>% 
+  ggplot(aes(x = mean_visits, y = mean_spend, colour = region)) +
+  geom_point()
+```
+
+```{r}
+usa_visit_spend_region %>% 
+  ggplot(aes(x = year, y = visits, colour = region, group = region)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019))
+```
+
+```{r}
+usa_visit_spend_region %>% 
+  ggplot(aes(x = year, y = spend, colour = region, group = region)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019))
+```
+
+```{r}
+library(leaflet)
+library(leafpop)
+```
+
+```{r}
+
+pal <- colorNumeric(
+  palette = "Reds",
+  domain = usa_visit_spend_region$visits)
+
+usa_visit_spend_region %>%
+  filter(year == 2019) %>% 
+  leaflet() %>%
+  addTiles() %>% 
+  addCircleMarkers(lng = ~long.x,
+                   lat = ~lat.x,
+                   color = ~pal(visits)) %>% 
+                   # popup = ~paste(location, "<br> Spend:", spend, "<br> Visits:", visits)) %>% 
+  addLegend(position = "bottomright", pal = geo_palette, values = ~visits, opacity = 2, title = "Visits") %>% 
+  addControl(position = "topright", html = title)
+```
+
+----------------------------------------------------------------
+
+----------------------------------------------------------------
+
+```{r}
+scotland_regions <- st_read(dsn = "geo/", # Data Source Name/Path
+                          layer = "SG_ScottishPoliceDivisions_2019")
+```
+
+```{r}
+glimpse(scotland_regions)
+```
+
+```{r}
+scotland_regions$PDivName
+```
+
+```{r}
+ggplot(scotland_regions) +
+  geom_sf(fill = "antiquewhite")
 ```

### 2023-06-13 scripts/cleaning_script.R

@@ -193,7 +193,8 @@ usa_spend_2009_2019_clean <- usa_spend_2009_2019 %>%
   mutate(year = str_remove(year, "x"))
 
 usa_visit_spend_region <- usa_visitors_2009_2019_clean %>% inner_join(usa_spend_2009_2019_clean, 
-                                                          by=c("region", "year"))
+                                                          by=c("region", "year")) %>% 
+  select(-lat.y, -long.y)
 
 # Clean Activities Data ------------------------------------------------------------
 

### 2023-06-14 visit_scotland_notebook.Rmd
Activity Data Work

@@
 social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
-regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
+regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
 activities <- read_csv(here("data/clean_data/activities_clean.csv"))
@@
   ggplot(aes(x = year, y = visits, group = 1)) +
-  geom_line(size = 1, colour = "grey") +
+  geom_line(size = 1.5, colour = "grey") +
   geom_point(aes(colour = visits_change_label), 
@@
   labs(x = "\n Year",
-       y = "No. of Visits (Million) \n",
-       title = "Number of Visits Over Time") +
+       y = "No. of Day Visits (Million) \n",
+       title = "Annual Number of Day Visits") +
   scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
+  theme(plot.title = element_text(size = 20, face = "bold"),
+        plot.subtitle = element_text(size = 10),
+        panel.background = element_rect(fill = "white"),
+        panel.grid = element_line(colour = "grey90", 
+                                  linetype = "dashed"))
 ```
@@
   group_by(age) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  arrange(age) %>% 
   ggplot() +
-  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
+  geom_col(aes(x = age, y = mean_visits, fill = age == "16-24 years"),
            show.legend = FALSE) +
@@
     x = "\n Age",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019") +
+    y = "Mean Visits per Year (Million) \n",
+    title = "Mean Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+age_demographics %>%
+  group_by(age) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  arrange(age) %>% 
+  ggplot() +
+  geom_col(aes(x = age, y = mean_exp, fill = age == "25-34 years"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Age",
+    y = "Mean Visits per Year (Million) \n",
+    title = "Mean Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+age_demographics %>%
+  group_by(age) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Age",
+    y = "Mean Annual Expenditure \n",
+    title = "Mean Annual Expenditure 2013-2019") +
   coord_flip()
@@
   group_by(employment_status) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot() +
+  geom_col(aes(x = employment_status, y = mean_exp, fill = employment_status == "Employed/self-employed (full or part time)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Employment",
+    y = "Mean Annual Spend \n",
+    title = "Mean Annual Spend 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+employment_demographics %>%
+  group_by(employment_status) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot() +
+  geom_col(aes(x = employment_status, y = mean_visits, fill = employment_status == "Employed/self-employed (full or part time)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Employment",
+    y = "Mean Annual Visits \n",
+    title = "Mean Annual Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+employment_demographics %>%
+  group_by(employment_status) %>% 
   summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
@@
     y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Employment")
+    title = "Mean Expenditure per Visit 2013-2019") +
+  coord_flip()
 ```
@@
     y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+    title = "Expenditure Per Visit % Diff, 2019 vs. 2013-2018 Avg.") +
   coord_flip() +
@@
   group_by(tourism_activity) %>%
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot() +
+  geom_col(aes(x = tourism_activity, y = mean_exp,
+               fill = tourism_activity == "Eating Out"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Annual Spend \n",
+    title = "Mean Annual Spend, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot() +
+  geom_col(aes(x = tourism_activity, y = mean_visits,
+               fill = tourism_activity == "Visited friends or family for leisure"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Annual Visits \n",
+    title = "Mean Annual Visits, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
   summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
   ggplot() +
-  geom_col(aes(x = reorder(tourism_activity, mean_exp_per_visit), y = mean_exp_per_visit,
+  geom_col(aes(x = tourism_activity, y = mean_exp_per_visit,
                fill = tourism_activity == "Shopping for Non-Regular Purchases"),
@@
   filter(year %in% c(2017, 2018, 2019)) %>% 
-  summarise(total_visits = sum(visits)) %>% 
-  select(total_visits)
+  summarise(mean_visits = mean(visits)) %>% 
+  select(mean_visits)
 
 tibble(a = c("Domestic", "International"),
-       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$total_visits)) %>% 
+       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$mean_visits)) %>% 
   ggplot() +

### 2023-06-14 scripts/cleaning_script.R

@@ -139,12 +139,31 @@ social_demographics_clean <- demographics %>%
 
 # Clean Regional Domestic Tourism Data (Overnights) ------------------------------------------------------------
 
-regional_domestic_tourism_clean <- regional_domestic_tourism %>%
-  filter(feature_code == "S92000003") %>%
+regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
+  filter(feature_code == "S92000003",
+         region_of_residence == "All of GB") %>%
   arrange(date_code) %>% 
   select(-c(measurement, units)) %>% 
   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
-  clean_names()
+  clean_names() %>% 
+  mutate(exp_per_visit = expenditure / visits,
+         exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
+         nights_change_label = case_when(nights > lag(nights) ~ "Increased",
+                                         nights < lag(nights) ~ "Decreased",
+                                         nights == lag(nights) ~ "No Change",
+                                         TRUE ~ "Starting Year"),
+         visits_change_label = case_when(visits > lag(visits) ~ "Increased",
+                                         visits < lag(visits) ~ "Decreased",
+                                         visits == lag(visits) ~ "No Change",
+                                         TRUE ~ "Starting Year"),
+         exp_change_label = case_when(expenditure > lag(expenditure) ~ "Increased",
+                                      expenditure < lag(expenditure) ~ "Decreased",
+                                      expenditure == lag(expenditure) ~ "No Change",
+                                      TRUE ~ "Starting Year"),
+         exp_per_visit_label = case_when(exp_per_visit > lag(exp_per_visit) ~ "Increased",
+                                         exp_per_visit < lag(exp_per_visit) ~ "Decreased",
+                                         exp_per_visit == lag(exp_per_visit) ~ "No Change",
+                                         TRUE ~ "Starting Year"))
 
 # Create International Passenger Survey Tibble  ------------------------------------------------------------
 
@@ -235,7 +254,7 @@ write_csv(children_demographics_clean, here("data/clean_data/children_demographi
 write_csv(car_demographics_clean, here("data/clean_data/car_demographics_clean.csv"))
[…]

### 2023-06-14 draft_work.Rmd
Restructured Project

@@
 ---
-title: "R Notebook"
+title: "Draft Work Notebook"
 output: html_notebook
 ---
+
+```{r}
+regional_domestic_tourism %>%
+  filter(feature_code != "S92000003",
+         region_of_residence == "All of GB") %>%
+  arrange(date_code) %>% 
+  select(-c(measurement, units)) %>% 
+  pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
+  clean_names() %>%
+  rename(year = date_code) %>% 
+  inner_join(local_authority_codes, by = "feature_code")
+
+```
+
+## Load Libraries
+
+```{r}
+library(tidyverse)
+library(here)
+library(modelr)
+library(ggfortify)
+```
+
+## Run Cleaning Script
+
+```{r}
+source(here("scripts/cleaning_script.R"))
+```
+
+## Read In Clean Data
+
+```{r}
+
+demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
+employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
+gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
+age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
+marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
+children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
+car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
+social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
+regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
+activities <- read_csv(here("data/clean_data/activities_clean.csv"))
+usa_visit_spend_region <- read_csv(here("data/clean_data/usa_visit_spend_region_clean.csv"))
+
+```
+
+## Temporal Analysis
+
+### Total Visits Over Time
+
+```{r}
+
+# Total Visits Over Time
+
+demographics_all %>% 
+  ggplot(aes(x = year, y = visits, group = 1)) +
+  geom_line(size = 1.5, colour = "grey") +
+  geom_point(aes(colour = visits_change_label), 
+             show.legend = FALSE,
+             size = 4) +
+  labs(x = "\n Year",
+       y = "No. of Day Visits (Million) \n",
+       title = "Annual Number of Day Visits") +
+  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
+  theme(plot.title = element_text(size = 20, face = "bold"),
+        plot.subtitle = element_text(size = 10),
+        panel.background = element_rect(fill = "white"),
+        panel.grid = element_line(colour = "grey90", 
+                                  linetype = "dashed"))
+```
+
+### Total Expenditure Over Time
+
+```{r}
+
+# Total Expenditure Over Time
+
+demographics_all %>% 
+  ggplot(aes(x = year, y = expenditure, group = 1)) +
+  geom_line(size = 1, colour = "grey") +
+  geom_point(aes(colour = exp_change_label), 
+             show.legend = FALSE,
+             size = 4) +
+  labs(x = "\n Year",
+       y = "Expenditure (Million Pounds, GBP) \n",
+       title = "Expenditure Over Time") +
+  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+
+```
+### Expenditure Per Visit Over Time
+
+```{r}
+
+# Expenditure Per Visit Over Time
+
+demographics_all %>% 
+  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
+  geom_line(size = 1, colour = "grey") +
+  geom_point(aes(colour = exp_per_visit_label), 
+             show.legend = FALSE,
+             size = 4) +
+  labs(x = "\n Year",
+       y = "Expenditure (Million Pounds, GBP) per Visit (Millions) \n",
+       title = "Expenditure Per Visit \n") +
+  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+
+```
+
+## Demographic Analysis
+
+- Highest Mean Spend Per Visit (2013-2018) vs. 2019
+- Highest Mean Spend Per Visit.
+
+### Age
+
+Spend Per Visit Over Period: 45-54
+Spend Per Visit (2013-2018) vs. 2019: 
+- Increase in 25-34, 35-44, 55-64, 65+
+- Interesting decrease in 45-54 despite being highest mean across all years.
+
+Conclusion: May suggest that there is scope for growth in other age groups, but not in 45-54.
+
+```{r}
+age_demographics %>%
+  group_by(age) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  arrange(age) %>% 
+  ggplot() +
+  geom_col(aes(x = age, y = mean_visits, fill = age == "16-24 years"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Age",
+    y = "Mean Visits per Year (Million) \n",
+    title = "Mean Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+age_demographics %>%
+  group_by(age) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  arrange(age) %>% 
+  ggplot() +
+  geom_col(aes(x = age, y = mean_exp, fill = age == "25-34 years"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Age",
+    y = "Mean Visits per Year (Million) \n",
+    title = "Mean Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+age_demographics %>%
+  group_by(age) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = age, y = mean_exp_per_visit, fill = age == "45-54 years"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Age",
+    y = "Mean Annual Expenditure \n",
+    title = "Mean Annual Expenditure 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+
+age_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(age, is_2019) %>%
+  arrange(age) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(age, difference_exp_per_visit), y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Age",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+
+```
+
+### Gender
+
+Highest Mean Spend Per Visit Over Period: Little difference between male and female spend per visit.
+Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
+
+Conclusion: Little difference between genders, both show potential for growth.
+
+```{r}
+gender_demographics %>%
+  group_by(gender) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Gender",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019")
+```
+
+```{r}
+gender_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(gender, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = gender, y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Gender",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+### Marital Status
+
+Highest Mean Spend Per Visit Over Period: Married people spend more than un-married.
+Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
+
+Conclusion: Although married people were already spending the most per visit, their spend increased by a larger amount in 2019 than un-married people, suggesting there is still plenty of room for growth.
+
+```{r}
+marital_demographics %>%
+  group_by(marital_status) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = marital_status, y = mean_exp_per_visit, fill = marital_status == "Married"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Marital Status",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019",
+    subtitle = "By Marital Status")
+```
+
+```{r}
+marital_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(marital_status, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = marital_status, y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Marital Status",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+### Children
+
+Highest Mean Spend Per Visit Over Period: People with children spent more per visit than people without.
+Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
+
+Conclusion: Although people with children spend more per visit than people without, both categories increased spending per visit in 2019 suggesting there is room for growth in both areas.
+
+```{r}
+children_demographics %>%
+  group_by(children) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = children, y = mean_exp_per_visit, fill = children == "Yes - Children"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Children",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019",
+    subtitle = "By Children")
+```
+
+```{r}
+children_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(children, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = children, y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Children",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+### Employment
+
+Highest Mean Spend Per Visit Over Period: People in employment have the highest average spend per visit.
+Mean Spend Per Visit (2013-2018) vs. 2019: All Increased.
+
+Conclusion: Although people in employment have the highest spend per visit there was rleatively little growth in this area in 2019.
+By comparison both other categories increase their spend per visit suggesting theire is potential for growth in these areas.
+
+```{r}
+employment_demographics %>%
+  group_by(employment_status) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot() +
+  geom_col(aes(x = employment_status, y = mean_exp, fill = employment_status == "Employed/self-employed (full or part time)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Employment",
+    y = "Mean Annual Spend \n",
+    title = "Mean Annual Spend 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+employment_demographics %>%
+  group_by(employment_status) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot() +
+  geom_col(aes(x = employment_status, y = mean_visits, fill = employment_status == "Employed/self-employed (full or part time)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Employment",
+    y = "Mean Annual Visits \n",
+    title = "Mean Annual Visits 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+employment_demographics %>%
+  group_by(employment_status) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Employment",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+employment_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(employment_status, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Employment Status",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Diff, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+
+```
+
+### Car Access
+
+Highest Mean Spend Per Visit Over Period: People with access to a car spent more per visit on average.
+Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
+
+Conclusion: Although people with access to a car spend more per visit, spend per visit amongst those without access to a car increased by more than those with a car.
+Highlights potential growth in this areas and particuarly related to transport.
+
+```{r}
+car_demographics %>%
+  group_by(access_to_car) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Car Access",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019",
+    subtitle = "By Car Access")
+```
+```{r}
+car_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(access_to_car, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = access_to_car, y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Access To Car",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+### Social Grade
+
+AB	Higher & intermediate managerial, administrative, professional occupations.
+C1	Supervisory, clerical & junior managerial, administrative, professional occupations.
+C2	Skilled manual occupations.
+DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations.
+
+```{r}
+social_demographics %>%
+  group_by(social_grade) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = reorder(social_grade, mean_exp_per_visit), y = mean_exp_per_visit, fill = social_grade == "AB"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Social Gradee",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+social_demographics %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(social_grade, is_2019) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(social_grade, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Social Grade",
+    y = "% Difference \n",
+    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+## Activities
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot() +
+  geom_col(aes(x = tourism_activity, y = mean_exp,
+               fill = tourism_activity == "Eating Out"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Annual Spend \n",
+    title = "Mean Annual Spend, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot() +
+  geom_col(aes(x = tourism_activity, y = mean_visits,
+               fill = tourism_activity == "Visited friends or family for leisure"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Annual Visits \n",
+    title = "Mean Annual Visits, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>%
+  group_by(tourism_activity) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  ggplot() +
+  geom_col(aes(x = tourism_activity, y = mean_exp_per_visit,
+               fill = tourism_activity == "Shopping for Non-Regular Purchases"),
+           show.legend = FALSE) +
+  scale_fill_manual(values = c("FALSE" = "grey40",
+                               "TRUE" = "forestgreen")) +
+  labs(
+    x = "\n Activity",
+    y = "Mean Expenditure per Visit \n",
+    title = "Mean Expenditure per Visit, 2013-2019") +
+  coord_flip()
+```
+
+```{r}
+activities %>% 
+  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
+  group_by(tourism_activity, is_2019) %>%
+  arrange(tourism_activity) %>%
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
+         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
+         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
+  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
+  ggplot(aes(x = reorder(tourism_activity, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
+  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
+  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
+  scale_fill_manual(values = c("Increased" = "forestgreen",
+                               "Decreased" = "firebrick")) +
+  labs(
+    x = "\n Activity",
+    y = "% Difference \n",
+    title = "Mean Expenditure per Visit, 2019 vs. 2013-2018 Avg.") +
+  coord_flip() +
+  scale_y_continuous(labels = scales::percent_format(scale = 1))
+```
+
+## Domestic & International Visitors
+
+### Domestic vs. International
+
+```{r}
+domestic_2017_2019_visits <- regional_domestic_tourism %>% 
+  filter(date_code == "2017-2019",
+         region_of_residence == "All of GB") %>% 
+  select(visits)
+
+international_2017_2019_visits <- international_visits %>%
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2017, 2018, 2019)) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  select(mean_visits)
+
+tibble(a = c("Domestic", "International"),
+       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$mean_visits)) %>% 
+  ggplot() +
+  geom_col(aes(x = a, y = b)) +
+  labs(
+    x = "",
+    y = "Visits \n",
+    title = "Domestic vs. International Visits",
+    subtitle = "2017-2019")
+```
+
+```{r}
+domestic_2017_2019_spend <- regional_domestic_tourism %>% 
+  filter(date_code == "2017-2019",
+         region_of_residence == "All of GB") %>% 
+  select(expenditure)
+
+international_2017_2019_spend <- international_visits %>%
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2017, 2018, 2019)) %>% 
+  summarise(total_visits = sum(visits),
+            total_spend = sum(spend),
+            exp_per_visit = total_spend / total_visits) %>% 
+  select(total_spend)
+
+tibble(a = c("Domestic", "International"),
+       b = c(domestic_2017_2019_spend$expenditure, international_2017_2019_spend$total_spend)) %>% 
+  ggplot() +
+  geom_col(aes(x = a, y = b)) +
+  labs(
+    x = "",
+    y = "Expenditure \n",
+    title = "Domestic vs. International Expenditure",
+    subtitle = "2017-2019")
+```
+
+### International
+
+#### Summary
+
+```{r}
+ips_2002_2019 %>%
+  summarise(cor(spend, visits))
+```
+
+```{r}
+model_ips <- lm(formula = spend ~ visits, data = ips_2002_2019)
+summary(model_ips)
+```
+
+```{r}
+autoplot(model_ips)
+```
+
+```{r}
+ips_2002_2019 %>%
+  add_predictions(model_ips) %>%
+  add_residuals(model_ips) %>% 
+  ggplot(aes(x = visits, y = spend)) +
+  geom_point() +
+  geom_line(aes(y = pred), col = "red") +
+  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
+  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 2.46e-08") +
+  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.864 / Residual Standard Error: 195.2") +
+  labs(
+    x = "Visits (Million)",
+    y = "Expenditure (£Million) \n",
+    title = "Scotland: International Visits vs. Spend",
+    subtitle = "2002-2019")
+```
+
+#### By Country
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(country %in% c("USA", "Germany", "Australia", "France", "China"),
+         year %in% c(2013, 2014, 2015, 2016, 2017, 
+                                2018, 2019)) %>% 
+  group_by(year, country) %>% 
+  summarise(total_spend = sum(spend)) %>% 
+  ggplot(aes(x = year, y = total_spend, colour = country)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
+                                2018, 2019)) +
+  labs(x = "\n Year",
+       y = "Expenditure (Million) \n",
+       title = "Expenditure by Country",
+       subtitle = "Top 5 Countries per Total Expenditure")
+```
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(country %in% c("USA", "Germany", "France", "Netherlands", "Australia"),
+         year %in% c(2013, 2014, 2015, 2016, 2017, 
+                                2018, 2019)) %>% 
+  group_by(year, country) %>% 
+  summarise(total_visits = sum(visits)) %>% 
+  ggplot(aes(x = year, y = total_visits, colour = country)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
+                                2018, 2019)) +
+  labs(x = "\n Year",
+       y = "Visits (Million) \n",
+       title = "Visits by Country",
+       subtitle = "Top 5 Countries per Visits")
+```
+
+#### USA
+
+```{r}
+ips_2002_2019_usa %>%
+  summarise(cor(spend, visits))
+```
+
+```{r}
+model_ips_usa <- lm(formula = spend ~ visits, data = ips_2002_2019_usa)
+summary(model_ips_usa)
+```
+
+Model: spend ~ visits
+
+Interpretation: ~83% of the variation in expenditure can be explained by the number of visits.
+
+Question: USA visits increased by 11.5789% between 2018 and 2019 to 636 Million. If this percentage increase in visits was replicated in 2020 (709.642m), what would our model predict for expenditure?
+
+Answer: If USA visits were increased as above, the model would predict expenditure of ~£723m (Low Estimate ~£655m, High Estimate ~£791m)
+
+As calculated below.
+
+Step 1.
+outcome = b0 + b1 * 1st Predictor
+
+Step 2.
+expenditure = b0(intercept) + b1(coefficient) * 1st Predictor
+
+Step 3.
+expenditure = b0(intercept) + b1(coefficient) * `visits`
+
+Step 4.
+expenditure = -195.9631 + 1.2953 * `709.642`
+
+Step 5.
+expenditure = 723.2287 (Low Estimate 655.3287, High Estimate 791.1287)
+
+```{r}
+
+predict_at <- data.frame(visits = c(709.642))
+
+# get predicted heights at those sample_weights
+predict(model_ips_usa, newdata = predict_at)
+```
+
+```{r}
+723.2287  + c(-67.9, 67.9)
+```
+
+```{r}
+ips_2002_2019_usa %>%
+  add_predictions(model_ips_usa) %>%
+  add_residuals(model_ips_usa) %>% 
+  ggplot(aes(x = visits, y = spend)) +
+  geom_point() +
+  geom_line(aes(y = pred), col = "red") +
+  labs(
+    x = "Visits (Million)",
+    y = "Expenditure (£Million) \n",
+    title = "Scotland: USA Visits vs. Spend",
+    subtitle = "2002-2019")
+```
+
+```{r}
+autoplot(model_ips_usa)
+```
 

### 2023-06-14 visit_scotland_notebook.Rmd
Restructured Project

--- 2023-06-13 visit_scotland_notebook.Rmd
@@
 library(here)
-library(modelr)
-library(ggfortify)
+library(sf)
+library(infer)
 ```
@@
 
-demographics_all <- read_csv(here("data/clean_data/all_demographics_clean.csv"))
-employment_demographics <- read_csv(here("data/clean_data/employment_demographics_clean.csv"))
-gender_demographics <- read_csv(here("data/clean_data/gender_demographics_clean.csv"))
-age_demographics <- read_csv(here("data/clean_data/age_demographics_clean.csv"))
-marital_demographics <- read_csv(here("data/clean_data/marital_status_demographics_clean.csv"))
-children_demographics <- read_csv(here("data/clean_data/children_demographics_clean.csv"))
-car_demographics <- read_csv(here("data/clean_data/car_demographics_clean.csv"))
-social_demographics <- read_csv(here("data/clean_data/social_demographics_clean.csv"))
-regional_domestic_tourism <- read_csv(here("data/clean_data/regional_domestic_tourism_clean.csv"))
-activities <- read_csv(here("data/clean_data/activities_clean.csv"))
+regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
+regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
+local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
 
@@
 
-## Temporal Analysis
+## Trends Over Time
 
-### Total Visits Over Time
+### Domestic Tourism / Visits
 
@@
 
-# Total Visits Over Time
-
-demographics_all %>% 
-  ggplot(aes(x = year, y = visits, group = 1)) +
-  geom_line(size = 1, colour = "grey") +
+regional_domestic_tourism_all %>%
+  ggplot(aes(x = date_code, y = visits)) +
+  geom_line(group = 1) +
   geom_point(aes(colour = visits_change_label), 
@@
              size = 4) +
-  labs(x = "\n Year",
-       y = "No. of Visits (Million) \n",
-       title = "Number of Visits Over Time") +
-  scale_y_continuous(limits = c(0, 200), breaks = c(0, 100, 200)) +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+  labs(x = "\n Year Range",
+       y = "Visitors (Thousands) \n",
+       title = "Average Annual Number of Domestic Vistors",
+       subtitle = "3 Year Average")
+
 ```
 
-### Total Expenditure Over Time
+### Domestic Tourism / Expenditure
 
@@
 
-# Total Expenditure Over Time
-
-demographics_all %>% 
-  ggplot(aes(x = year, y = expenditure, group = 1)) +
-  geom_line(size = 1, colour = "grey") +
+regional_domestic_tourism_all %>%
+  ggplot(aes(x = date_code, y = expenditure)) +
+  geom_line(group = 1) +
   geom_point(aes(colour = exp_change_label), 
@@
              size = 4) +
-  labs(x = "\n Year",
-       y = "Expenditure (Million) \n",
-       title = "Expenditure Over Time") +
-  scale_y_continuous(limits = c(0, 6500), breaks = c(0, 2000, 4000, 6000)) +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+  labs(x = "\n Year Range",
+       y = "Expenditure (Million GBP) \n",
+       title = "Average Annual Expenditure of Domestic Vistors",
+       subtitle = "3 Year Average")
 
 ```
-### Expenditure Per Visit Over Time
+### Domestic Tourism / Nights Stayed
 
@@
 
-# Expenditure Per Visit Over Time
+regional_domestic_tourism_all %>%
+  ggplot(aes(x = date_code, y = nights)) +
+  geom_line(group = 1) +
+  geom_point(aes(colour = nights_change_label), 
+             show.legend = FALSE,
+             size = 4) +
+  labs(x = "\n Year Range",
+       y = "Nights (Thousands) \n",
+       title = "Average Annual Nights Stayed by Domestic Vistors",
+       subtitle = "3 Year Average")
 
-demographics_all %>% 
-  ggplot(aes(x = year, y = exp_per_visit, group = 1)) +
-  geom_line(size = 1, colour = "grey") +
+```
+
+### Domestic Tourism / Expenditure per Visit
+
+```{r}
+regional_domestic_tourism_all %>%
+  ggplot(aes(x = date_code, y = exp_per_visit)) +
+  geom_line(group = 1) +
   geom_point(aes(colour = exp_per_visit_label), 
@@
              size = 4) +
-  labs(x = "\n Year",
-       y = "Expenditure (Millions) per Visit (Millions) \n",
-       title = "Expenditure To Visit Ratio \n") +
-  scale_y_continuous(limits = c(0, 60), breaks = c(0, 20, 40, 60)) +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 2018, 2019))
+  labs(x = "\n Year Range",
+       y = "3x Year Average Expenditure per Visit (Thousands) \n",
+       title = "Average Expenditure Per Visit Domestic Vistors",
+       subtitle = "3 Year Average")
+```
+
+### Which Regions Are Domestic Tourists Visiting
+
+#### Average Visits By Region
+
+##### Stats
+
+```{r}
+
+regional_domestic_tourism_all %>% 
+  summarise(mean_annual_visits = mean(visits))
+
+# Mean Annual Visits: ~12,337,000
+
+regional_domestic_tourism_all %>%
+  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
+  summarise(mean_visits = mean(visits)) %>% 
+  get_confidence_interval(level = 0.95, type = "percentile")
+
+# 95% CI: 12,175,250 - 12,507,590
+```
+
+##### Map
+
+```{r}
+
+regional_data_joined %>% 
+  group_by(year, code) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot(aes(fill = mean_visits)) + 
+  geom_sf() +
+  labs(
+    x = "Longitude",
+    y = "Latitude",
+    title = "Average Annual Number of Domestic Vistors",
+    subtitle = "By Region",
+    fill = "Visits (Thousands)"
+  ) +
+  theme(panel.background = element_rect(fill = "white"))
 
@@
 
-## Demographic Analysis
+#### Expenditure by Region
 
-- Highest Mean Spend Per Visit (2013-2018) vs. 2019
-- Highest Mean Spend Per Visit.
-
-### Age
-
-Spend Per Visit Over Period: 45-54
-Spend Per Visit (2013-2018) vs. 2019: 
-- Increase in 25-34, 35-44, 55-64, 65+
-- Interesting decrease in 45-54 despite being highest mean across all years.
-
-Conclusion: May suggest that there is scope for growth in other age groups, but not in 45-54.
+##### Stats
 
 ```{r}
-age_demographics %>%
-  group_by(age) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = reorder(age, mean_exp_per_visit), y = mean_exp_per_visit, fill = age == "45-54 years"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Age",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Age Group") +
-  coord_flip()
+regional_domestic_tourism_all %>% 
+  summarise(mean_annual_exp = mean(expenditure))
+
+# Mean Annual Expenditure:
+
+regional_domestic_tourism_all %>%
+  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
+  summarise(mean_annual_exp = mean(expenditure)) %>% 
+  get_confidence_interval(level = 0.95, type = "percentile")
+
+# 95% CI: 1
 ```
 
+##### Map
+
 ```{r}
-
-age_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(age, is_2019) %>%
-  arrange(age) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = reorder(age, difference_exp_per_visit), y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
+regional_data_joined %>% 
+  group_by(year, code) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot(aes(fill = mean_exp)) + 
+  geom_sf() +
   labs(
-    x = "\n Age",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  coord_flip() +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-
+    x = "Longitude",
+    y = "Latitude",
+    title = "Average Annual Expenditure of Domestic Vistors",
+    subtitle = "By Region",
+    fill = "Expenditure (Million GBP)"
+  ) +
+  theme(panel.background = element_rect(fill = "white"))
 ```
 
-### Gender
-
-Highest Mean Spend Per Visit Over Period: Little difference between male and female spend per visit.
-Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
-
-Conclusion: Little difference between genders, both show potential for growth.
-
-```{r}
-gender_demographics %>%
-  group_by(gender) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = gender, y = mean_exp_per_visit, fill = gender == "Male"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Gender",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019")
-```
-
-```{r}
-gender_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(gender, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = gender, y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Gender",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-```
-
-### Marital Status
-
-Highest Mean Spend Per Visit Over Period: Married people spend more than un-married.
-Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
-
-Conclusion: Although married people were already spending the most per visit, their spend increased by a larger amount in 2019 than un-married people, suggesting there is still plenty of room for growth.
-
-```{r}
-marital_demographics %>%
-  group_by(marital_status) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = marital_status, y = mean_exp_per_visit, fill = marital_status == "Married"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Marital Status",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Marital Status")
-```
-
-```{r}
-marital_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(marital_status, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = marital_status, y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Marital Status",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-```
-
-### Children
-
-Highest Mean Spend Per Visit Over Period: People with children spent more per visit than people without.
-Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
-
-Conclusion: Although people with children spend more per visit than people without, both categories increased spending per visit in 2019 suggesting there is room for growth in both areas.
-
-```{r}
-children_demographics %>%
-  group_by(children) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = children, y = mean_exp_per_visit, fill = children == "Yes - Children"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Children",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Children")
-```
-
-```{r}
-children_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(children, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = children, y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Children",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-```
-
-### Employment
-
-Highest Mean Spend Per Visit Over Period: People in employment have the highest average spend per visit.
-Mean Spend Per Visit (2013-2018) vs. 2019: All Increased.
-
-Conclusion: Although people in employment have the highest spend per visit there was rleatively little growth in this area in 2019.
-By comparison both other categories increase their spend per visit suggesting theire is potential for growth in these areas.
-
-```{r}
-employment_demographics %>%
-  group_by(employment_status) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = employment_status, y = mean_exp_per_visit, fill = employment_status == "Employed/self-employed (full or part time)"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Employment",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Employment")
-```
-
-```{r}
-employment_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(employment_status, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = reorder(employment_status, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Employment Status",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  coord_flip() +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-
-```
-
-### Car Access
-
-Highest Mean Spend Per Visit Over Period: People with access to a car spent more per visit on average.
-Mean Spend Per Visit (2013-2018) vs. 2019: Both Increased.
-
-Conclusion: Although people with access to a car spend more per visit, spend per visit amongst those without access to a car increased by more than those with a car.
-Highlights potential growth in this areas and particuarly related to transport.
-
-```{r}
-car_demographics %>%
-  group_by(access_to_car) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = access_to_car, y = mean_exp_per_visit, fill = access_to_car == "Access to car (1+)"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Car Access",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019",
-    subtitle = "By Car Access")
-```
-```{r}
-car_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(access_to_car, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = access_to_car, y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Access To Car",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-```
-
-### Social Grade
-
-AB	Higher & intermediate managerial, administrative, professional occupations.
-C1	Supervisory, clerical & junior managerial, administrative, professional occupations.
-C2	Skilled manual occupations.
-DE	Semi-skilled & unskilled manual occupations, Unemployed and lowest grade occupations.
-
-```{r}
-social_demographics %>%
-  group_by(social_grade) %>% 
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  ggplot() +
-  geom_col(aes(x = reorder(social_grade, mean_exp_per_visit), y = mean_exp_per_visit, fill = social_grade == "AB"),
-           show.legend = FALSE) +
-  scale_fill_manual(values = c("FALSE" = "grey40",
-                               "TRUE" = "forestgreen")) +
-  labs(
-    x = "\n Social Gradee",
-    y = "Mean Expenditure per Visit \n",
-    title = "Mean Expenditure per Visit 2013-2019") +
-  coord_flip()
-```
-
-```{r}
-social_demographics %>% 
-  mutate(is_2019 = if_else(year == 2019, "2019", "2013-2018")) %>% 
-  group_by(social_grade, is_2019) %>%
-  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
-  mutate(difference_exp_per_visit = mean_exp_per_visit - lag(mean_exp_per_visit),
-         difference_exp_per_visit_pct = (mean_exp_per_visit - lag(mean_exp_per_visit)) / lag(mean_exp_per_visit) * 100,
-         difference_exp_per_visit_label = if_else(difference_exp_per_visit > 0, "Increased", "Decreased")) %>% 
-  filter(difference_exp_per_visit != is.na(difference_exp_per_visit)) %>% 
-  ggplot(aes(x = reorder(social_grade, difference_exp_per_visit_pct), y = difference_exp_per_visit_pct)) +
-  geom_col(aes(fill = difference_exp_per_visit_label), show.legend = FALSE) +
-  # geom_text(aes(label = str_c(floor(difference_exp_per_visit_pct), "%"), vjust = -0.5)) +
-  scale_fill_manual(values = c("Increased" = "forestgreen",
-                               "Decreased" = "firebrick")) +
-  labs(
-    x = "\n Social Grade",
-    y = "% Difference \n",
-    title = "Expenditure Per Visit % Difference, 2019 vs. 2013-2018 Avg.") +
-  coord_flip() +
-  scale_y_continuous(labels = scales::percent_format(scale = 1))
-```
-
-## Domestic & International Visitors
-
-### Domestic vs. International
-
-```{r}
-domestic_2017_2019_visits <- regional_domestic_tourism %>% 
-  filter(date_code == "2017-2019",
-         region_of_residence == "All of GB") %>% 
-  select(visits)
-
-international_2017_2019_visits <- international_visits %>%
-  select(-c(quarter, age, sample)) %>%
-  filter(year %in% c(2017, 2018, 2019)) %>% 
-  summarise(total_visits = sum(visits)) %>% 
-  select(total_visits)
-
-tibble(a = c("Domestic", "International"),
-       b = c(domestic_2017_2019_visits$visits, international_2017_2019_visits$total_visits)) %>% 
-  ggplot() +
-  geom_col(aes(x = a, y = b)) +
-  labs(
-    x = "",
-    y = "Visits \n",
-    title = "Domestic vs. International Visits",
-    subtitle = "2017-2019")
-```
-
-```{r}
-domestic_2017_2019_spend <- regional_domestic_tourism %>% 
-  filter(date_code == "2017-2019",
-         region_of_residence == "All of GB") %>% 
-  select(expenditure)
-
-international_2017_2019_spend <- international_visits %>%
-  select(-c(quarter, age, sample)) %>%
-  filter(year %in% c(2017, 2018, 2019)) %>% 
-  summarise(total_visits = sum(visits),
-            total_spend = sum(spend),
-            exp_per_visit = total_spend / total_visits) %>% 
-  select(total_spend)
-
-tibble(a = c("Domestic", "International"),
-       b = c(domestic_2017_2019_spend$expenditure, international_2017_2019_spend$total_spend)) %>% 
-  ggplot() +
-  geom_col(aes(x = a, y = b)) +
-  labs(
-    x = "",
-    y = "Expenditure \n",
-    title = "Domestic vs. International Expenditure",
-    subtitle = "2017-2019")
-```
-
-### International
-
-#### Summary
-
-```{r}
-ips_2002_2019 %>%
-  summarise(cor(spend, visits))
-```
-
-```{r}
-model_ips <- lm(formula = spend ~ visits, data = ips_2002_2019)
-summary(model_ips)
-```
-
-```{r}
-autoplot(model_ips)
-```
-
-```{r}
-ips_2002_2019 %>%
-  add_predictions(model_ips) %>%
-  add_residuals(model_ips) %>% 
-  ggplot(aes(x = visits, y = spend)) +
-  geom_point() +
-  geom_line(aes(y = pred), col = "red") +
-  annotate("text", x = 1675, y = 2500, label = "spend ~ visits") +
-  annotate("text", x = 1930, y = 2300, label = "b1 = 0.81800 / p-value = 2.46e-08") +
-  annotate("text", x = 2170, y = 2100, label = "R-Squared = 0.864 / Residual Standard Error: 195.2") +
-  labs(
-    x = "Visits (Million)",
-    y = "Expenditure (£Million) \n",
-    title = "Scotland: International Visits vs. Spend",
-    subtitle = "2002-2019")
-```
-
-#### By Country
-
-```{r}
-international_visits %>% 
-  select(-c(quarter, age, sample)) %>%
-  filter(country %in% c("USA", "Germany", "Australia", "France", "China"),
-         year %in% c(2013, 2014, 2015, 2016, 2017, 
-                                2018, 2019)) %>% 
-  group_by(year, country) %>% 
-  summarise(total_spend = sum(spend)) %>% 
-  ggplot(aes(x = year, y = total_spend, colour = country)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
-                                2018, 2019)) +
-  labs(x = "\n Year",
-       y = "Expenditure (Million) \n",
-       title = "Expenditure by Country",
-       subtitle = "Top 5 Countries per Total Expenditure")
-```
-
-```{r}
-international_visits %>% 
-  select(-c(quarter, age, sample)) %>%
-  filter(country %in% c("USA", "Germany", "France", "Netherlands", "Australia"),
-         year %in% c(2013, 2014, 2015, 2016, 2017, 
-                                2018, 2019)) %>% 
-  group_by(year, country) %>% 
-  summarise(total_visits = sum(visits)) %>% 
-  ggplot(aes(x = year, y = total_visits, colour = country)) +
-  geom_line() +
-  geom_point() +
-  scale_x_continuous(breaks = c(2013, 2014, 2015, 2016, 2017, 
-                                2018, 2019)) +
-  labs(x = "\n Year",
-       y = "Visits (Million) \n",
-       title = "Visits by Country",
-       subtitle = "Top 5 Countries per Visits")
-```
-
-#### USA
-
-```{r}
-ips_2002_2019_usa %>%
-  summarise(cor(spend, visits))
-```
-
-```{r}
-model_ips_usa <- lm(formula = spend ~ visits, data = ips_2002_2019_usa)
-summary(model_ips_usa)
-```
-
-Model: spend ~ visits
-
-Interpretation: ~83% of the variation in expenditure can be explained by the number of visits.
-
-Question: USA visits increased by 11.5789% between 2018 and 2019 to 636 Million. If this percentage increase in visits was replicated in 2020 (709.642m), what would our model predict for expenditure?
-
-Answer: If USA visits were increased as above, the model would predict expenditure of ~£723m (Low Estimate ~£655m, High Estimate ~£791m)
-
-As calculated below.
-
-Step 1.
-outcome = b0 + b1 * 1st Predictor
-
-Step 2.
-expenditure = b0(intercept) + b1(coefficient) * 1st Predictor
-
-Step 3.
-expenditure = b0(intercept) + b1(coefficient) * `visits`
-
-Step 4.
-expenditure = -195.9631 + 1.2953 * `709.642`
-
-Step 5.
-expenditure = 723.2287 (Low Estimate 655.3287, High Estimate 791.1287)
-
-```{r}
-
-predict_at <- data.frame(visits = c(709.642))
-
-# get predicted heights at those sample_weights
-predict(model_ips_usa, newdata = predict_at)
-```
-
-```{r}
-723.2287  + c(-67.9, 67.9)
-```
-
-```{r}
-ips_2002_2019_usa %>%
-  add_predictions(model_ips_usa) %>%
-  add_residuals(model_ips_usa) %>% 
-  ggplot(aes(x = visits, y = spend)) +
-  geom_point() +
-  geom_line(aes(y = pred), col = "red") +
-  labs(
-    x = "Visits (Million)",
-    y = "Expenditure (£Million) \n",
-    title = "Scotland: USA Visits vs. Spend",
-    subtitle = "2002-2019")
-```
-
-```{r}
-autoplot(model_ips_usa)
-```
-
-### Domestic
+### Line Plot Over Time

### 2023-06-14 scripts/cleaning_script.R

@@ -8,17 +8,19 @@ library(readxl)
 
 # Read In Raw Data ------------------------------------------------------------
 
-demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
-  clean_names()
-
 regional_domestic_tourism <- read_csv("data/raw_data/regional_domestic_tourism.csv") %>%
   clean_names()
 
-international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
-  clean_names()
+local_authority_codes <- read_csv("data/raw_data/local_authority_codes.csv")
 
-activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
-  clean_names()
+# demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
+#   clean_names()
+
+# international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
+#   clean_names()
+
+# activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
+#   clean_names()
 
 # domestic_day_visits <- read_excel("data/raw_data/gbdvs-2019-scotland-and-gb.xlsx") %>% 
 #   clean_names()
@@ -35,109 +37,109 @@ activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
 
 # Clean Demographic Data ------------------------------------------------------------
 
-all_demographics_clean <- demographics %>%
-  filter(age == "All", marital_status == "All", gender == "All", employment_status == "All",
-         children == "All",  access_to_car == "All", social_grade == "All") %>%
-  select(-c(measurement, units)) %>% 
-  pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
-  arrange(date_code) %>% 
-  mutate(exp_per_visit = Expenditure / Visits,
-         exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
-         visits_change_label = case_when(Visits > lag(Visits) ~ "Increased",
-                                         Visits < lag(Visits) ~ "Decreased",
-                                         Visits == lag(Visits) ~ "No Change",
-                                         TRUE ~ "Starting Year"),
-         exp_change_label = case_when(Expenditure > lag(Expenditure) ~ "Increased",
[…]

### 2023-06-14 draft_work.Rmd
Added Domestic Tourism Analysis, Started International Tourism Analysis

@@
   select(-c(quarter, age, sample)) %>%
-  filter(country %in% c("USA", "Germany", "Australia", "France", "China"),
-         year %in% c(2013, 2014, 2015, 2016, 2017, 
-                                2018, 2019)) %>% 
+  filter(year %in% c(2002, 2003, 2004, 2005, 2006, 2007,
+                     2008, 2009, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
   group_by(year, country) %>% 

### 2023-06-14 visit_scotland_notebook.Rmd
Added Domestic Tourism Analysis, Started International Tourism Analysis

@@
 
-### Which Regions Are Domestic Tourists Visiting
+## Domestic Tourism
 
 #### Average Visits By Region
+
+##### Over Time
+
+```{r}
+regional_domestic_tourism_individual %>%
+  filter(visits > 1000) %>% 
+  ggplot() +
+  geom_line(aes(x = year, y = visits, colour = local_authority, group = local_authority))
+```
 
@@
 
-# Mean Annual Visits: ~12,337,000
-
 regional_domestic_tourism_all %>%
@@
 
-# 95% CI: 12,175,250 - 12,507,590
 ```
@@
 regional_data_joined %>% 
-  group_by(year, code) %>% 
+  group_by(code) %>% 
   summarise(mean_visits = mean(visits)) %>% 
@@
 
+##### Over Time
+
+```{r}
+regional_domestic_tourism_individual %>%
+  filter(expenditure > 300) %>% 
+  ggplot() +
+  geom_line(aes(x = year, y = expenditure, colour = local_authority, group = local_authority))
+```
+
 ##### Stats
@@
 
-# Mean Annual Expenditure:
-
 regional_domestic_tourism_all %>%
@@
 
-# 95% CI: 1
 ```
@@
 regional_data_joined %>% 
-  group_by(year, code) %>% 
+  group_by(code) %>% 
   summarise(mean_exp = mean(expenditure)) %>% 
@@
 
-### Line Plot Over Time
+#### Spend Per Visit
+
+```{r}
+regional_domestic_tourism_individual %>%
+  filter(visits != 0,
+         expenditure != 0) %>% 
+  mutate(exp_per_visit = expenditure / visits, rm.na = TRUE) %>%
+  group_by(local_authority) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  arrange(desc(mean_exp_per_visit)) %>%
+  ggplot() +
+  geom_col(aes(x = reorder(local_authority, mean_exp_per_visit), y = mean_exp_per_visit,
+               fill = local_authority %in% c("City of Edinburgh", "Glasgow City", "Highland")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Region",
+    y = "Mean Expenditure per Visit (Million GBP / Thousand Visits)",
+    title = "Domestic Tourism Mean Expenditure per Visit",
+    subtitle = "By Region")
+```
+
+## International Tourism
+
+### Visit Stats
+
+```{r}
+international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(year) %>% 
+  summarise(sum_annual_visits = sum(visits)) %>% 
+  summarise(avg_annual_visits = mean(sum_annual_visits))
+
+international_visits_summary <- international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(year) %>% 
+  summarise(sum_annual_visits = sum(visits))
+
+international_visits_summary %>%
+  rep_sample_n(size = 11, replace = TRUE, reps = 5000) %>%
+  summarise(mean_visits = mean(sum_annual_visits)) %>% 
+  get_confidence_interval(level = 0.95, type = "percentile")
+
+```
+
+### Expenditure Stats
+
+```{r}
+international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(year) %>% 
+  summarise(sum_annual_exp = sum(spend)) %>% 
+  summarise(avg_annual_spend = mean(sum_annual_exp))
+
+international_spend_summary <- international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(year) %>% 
+  summarise(sum_annual_exp = sum(spend))
+
+international_spend_summary %>%
+  rep_sample_n(size = 11, replace = TRUE, reps = 5000) %>%
+  summarise(mean_spend = mean(sum_annual_exp)) %>% 
+  get_confidence_interval(level = 0.95, type = "percentile")
+
+```
+
+### Visitor Country of Residence
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019))) %>% 
+  group_by(year, country) %>% 
+  summarise(total_spend = sum(spend)) %>% 
+  ggplot(aes(x = year, y = total_spend, colour = country)) +
+  geom_line() +
+  geom_point() +
+  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
+  labs(x = "\n Year",
+       y = "Expenditure (Million) \n",
+       title = "Expenditure by Country",
+       subtitle = "Top 5 Countries per Total Expenditure")
+```

### 2023-06-14 scripts/cleaning_script.R

@@ -13,10 +13,10 @@ regional_domestic_tourism <- read_csv("data/raw_data/regional_domestic_tourism.c
 
 local_authority_codes <- read_csv("data/raw_data/local_authority_codes.csv")
 
-# demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
-#   clean_names()
+international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
+  clean_names()
 
-# international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
+# demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
 #   clean_names()
 
 # activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%

### 2023-06-15 visit_scotland_notebook.Rmd
Added Model for Case Study on Domestic Tourism

--- 2023-06-14 visit_scotland_notebook.Rmd
@@
 library(infer)
+library(ggridges)
+library(modelr)
 ```
@@
 regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
+regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
+international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
@@
 
-### Which Regions Are Domestic Tourists Visiting
+## Domestic Tourism
 
 #### Average Visits By Region
-
-##### Stats
-
-```{r}
-
-regional_domestic_tourism_all %>% 
-  summarise(mean_annual_visits = mean(visits))
-
-# Mean Annual Visits: ~12,337,000
-
-regional_domestic_tourism_all %>%
-  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
-  summarise(mean_visits = mean(visits)) %>% 
-  get_confidence_interval(level = 0.95, type = "percentile")
-
-# 95% CI: 12,175,250 - 12,507,590
-```
-
-##### Map
 
@@
 regional_data_joined %>% 
-  group_by(year, code) %>% 
+  group_by(code) %>% 
   summarise(mean_visits = mean(visits)) %>% 
   ggplot(aes(fill = mean_visits)) + 
-  geom_sf() +
+  geom_sf(colour = "grey90", size = 0.1) +
   labs(
@@
     subtitle = "By Region",
-    fill = "Visits (Thousands)"
-  ) +
-  theme(panel.background = element_rect(fill = "white"))
+    fill = "Visits (Thousands)") +
+  theme(panel.background = element_rect(fill = "white"),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        rect = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
 
@@
 
-##### Stats
+```{r}
+regional_data_joined %>% 
+  group_by(code) %>% 
+  summarise(mean_exp = mean(expenditure)) %>% 
+  ggplot(aes(fill = mean_exp)) + 
+  geom_sf(colour = "grey90", size = 0.1) +
+  labs(
+    x = "Longitude",
+    y = "Latitude",
+    title = "Average Annual Expenditure of Domestic Vistors",
+    subtitle = "By Region",
+    fill = "Expenditure (Million GBP)") +
+    theme(panel.background = element_rect(fill = "white"),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        rect = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+```
+
+#### Spend Per Visit
+
+##### Plot
 
 ```{r}
-regional_domestic_tourism_all %>% 
-  summarise(mean_annual_exp = mean(expenditure))
+regional_domestic_tourism_individual %>%
+  filter(visits != 0,
+         expenditure != 0) %>% 
+  mutate(exp_per_visit = expenditure / visits, rm.na = TRUE) %>%
+  group_by(local_authority) %>% 
+  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
+  arrange(desc(mean_exp_per_visit)) %>%
+  ggplot() +
+  geom_col(aes(x = reorder(local_authority, mean_exp_per_visit), y = mean_exp_per_visit,
+               fill = local_authority %in% c("City of Edinburgh", "Glasgow City", "Highland")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Region",
+    y = "Mean Expenditure per Visit (Million GBP / Thousand Visits)",
+    title = "Domestic Tourism Mean Expenditure per Visit",
+    subtitle = "By Region")
+```
 
-# Mean Annual Expenditure:
+#### Nights Stayed
 
-regional_domestic_tourism_all %>%
-  rep_sample_n(size = 12, replace = TRUE, reps = 5000) %>%
-  summarise(mean_annual_exp = mean(expenditure)) %>% 
-  get_confidence_interval(level = 0.95, type = "percentile")
+##### Plot
 
-# 95% CI: 1
+```{r}
+regional_domestic_tourism_individual %>% 
+  mutate(nights_per_visit = nights / visits) %>% 
+  group_by(local_authority) %>% 
+  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
+  ggplot() +
+  geom_col(aes(x = reorder(local_authority, mean_nights_per_visit), y = mean_nights_per_visit,
+               fill = local_authority %in% c("Shetland Islands", "Orkney Islands", "Na h-Eileanan Siar",
+                                             "City of Edinburgh", "Glasgow City")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Region",
+    y = "Avg. Nights per Visit",
+    title = "Domestic Tourism Avg. Nights per Visit",
+    subtitle = "By Region")
 ```
@@
 regional_data_joined %>%
-  group_by(year, code) %>% 
-  summarise(mean_exp = mean(expenditure)) %>% 
-  ggplot(aes(fill = mean_exp)) + 
-  geom_sf() +
+  mutate(nights_per_visit = nights / visits) %>% 
+  group_by(local_authority) %>% 
+  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
+  ggplot(aes(fill = mean_nights_per_visit)) + 
+  geom_sf(colour = "grey90", size = 0.1) +
   labs(
@@
     y = "Latitude",
-    title = "Average Annual Expenditure of Domestic Vistors",
+    title = "Domestic Tourism Mean Nights per Visit",
     subtitle = "By Region",
-    fill = "Expenditure (Million GBP)"
+    fill = "Mean Nights per Visit"
   ) +
-  theme(panel.background = element_rect(fill = "white"))
+  theme(panel.background = element_rect(fill = "white"),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        rect = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+
 ```
 
-### Line Plot Over Time
+#### Marketing Edinburgh to Domestic Tourists: Mini Case Study
+
+##### Visits by Country of Residence
+
+```{r}
+regional_domestic_tourism_non_gb_clean %>%
+  filter(local_authority %in% c("City of Edinburgh")) %>% 
+  ggplot(aes(x = visits, y = region_of_residence, fill = region_of_residence == "Scotland")) +
+  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
+  theme_ridges() +
+  theme(axis.title.y = element_blank()) +
+  scale_fill_manual(values = c("FALSE" = "#1d1d65",
+                               "TRUE" = "#540453")) +
+  labs(
+    title = "Distribution of Annual Visits by Country of Residence",
+    subtitle = "Edinburgh",
+    x = "Visits (Thousands)")
+```
+
+##### Spend Per Visit by Country of Residence
+
+```{r}
+regional_domestic_tourism_non_gb_clean %>%
+  filter(local_authority %in% c("City of Edinburgh")) %>%
+  mutate(exp_per_visit = expenditure / visits) %>% 
+  ggplot(aes(x = exp_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
+  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
+  theme_ridges() +
+  theme(axis.title.y = element_blank()) +
+  scale_fill_manual(values = c("FALSE" = "#1d1d65",
+                               "TRUE" = "#540453")) +
+  labs(
+    title = "Distribution of Expenditure per Visit by Country of Residence",
+    subtitle = "Edinburgh",
+    x = "Expenditure per Visit (Million GBP / Thousand Visits)")
+```
+
+##### Nights by Country of Residence
+
+```{r}
+regional_domestic_tourism_non_gb_clean %>%
+  filter(local_authority %in% c("City of Edinburgh")) %>% 
+  mutate(nights_per_visit = nights / visits) %>%
+  ggplot(aes(x = nights_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
+  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
+  theme_ridges() +
+  theme(axis.title.y = element_blank()) +
+  scale_fill_manual(values = c("FALSE" = "#1d1d65",
+                               "TRUE" = "#540453")) +
+  labs(
+    title = "Distribution of Nights by Country of Residence",
+    subtitle = "Edinburgh",
+    x = "Nights")
+```
+
+##### Linear Model: Predict Spend by Visits & Nights?
+
+```{r}
+regional_domestic_tourism_non_gb_clean %>% 
+  filter(local_authority == "City of Edinburgh",
+         region_of_residence == "England") %>% 
+  summarise(cor(expenditure, visits))
+```
+
+```{r}
+regional_domestic_tourism_non_gb_clean %>% 
+  filter(local_authority == "City of Edinburgh",
+         region_of_residence == "England") %>% 
+  summarise(cor(expenditure, nights))
+```
+
+```{r}
+edinburgh_england <- regional_domestic_tourism_non_gb_clean %>% 
+  filter(local_authority == "City of Edinburgh",
+         region_of_residence == "England")
+```
+
+```{r}
+model_edinburgh <- lm(formula = expenditure ~ visits, data = edinburgh_england)
+summary(model_edinburgh)
+```
+
+```{r}
+edinburgh_england %>%
+  add_predictions(model_edinburgh) %>%
+  add_residuals(model_edinburgh) %>% 
+  ggplot(aes(x = visits, y = expenditure)) +
+  geom_point() +
+  geom_line(aes(y = pred), col = "#970061", size = 1) +
+  labs(
+    x = "Visits (Thousands)",
+    y = "Expenditure (Million GBP)",
+    title = "English Based Visitors To Edinburgh: Expenditure / Visits",
+    subtitle = "Based On 3 Year Annual Averages Between 2009-2019")
+```
+Model: spend ~ visits
+
+Interpretation: ~97% of the variation in expenditure can be explained by the number of visits.
+
+Question: The largest increase in visitor numbers is from 2009-2011 Avg.
+to 2010-2012 Avg.
+~6%.
+If this percentage increase in visits was replicated in based on the most recent set of figures resulting in ~1803 (Thousand) visitors - what would the model predict for expenditure?
+
+Answer: If visits were increased as above, the model would predict expenditure of ~632 Million GBP (Low Estimate ~620, High Estimate ~644)
+
+As calculated below.
+
+Step 1.
+outcome = b0 + b1 * 1st Predictor
+
+Step 2.
+expenditure = b0(intercept) + b1(coefficient) * 1st Predictor
+
+Step 3.
+expenditure = b0(intercept) + b1(coefficient) * `visits`
+
+Step 4.
+expenditure = -493.61749 + 0.62423 * `1803`
+
+Step 5.
+expenditure = ~632 (Low Estimate ~620, High Estimate ~644)
+
+```{r}
+632 + c(-12.34, 12.34)
+```
+
+## International Tourism
+
+### Visit Stats
+
+```{r}
+international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(year) %>% 
+  summarise(sum_annual_visits = sum(visits)) %>% 
+  summarise(avg_annual_visits = mean(sum_annual_visits))
+
+```
+
+### Expenditure Stats
+
+```{r}
+international_visits %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(year) %>% 
+  summarise(sum_annual_exp = sum(spend)) %>% 
+  summarise(avg_annual_spend = mean(sum_annual_exp))
+
+```
+
+### Visitors by Country of Residence
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(country) %>% 
+  summarise(total_visits = sum(visits)) %>%
+  slice_max(total_visits, n = 20) %>% 
+  ggplot(aes(x = reorder(country, total_visits), y = total_visits)) +
+  geom_col(aes(x = reorder(country, total_visits), y = total_visits,
+               fill = country %in% c("USA")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Country",
+    y = "Total Visits (Thousands)",
+    title = "International Tourism: Total Visits (2002-2009)",
+    subtitle = "Top 20")
+```
+
+### Spend by Country of Residence
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(country) %>% 
+  summarise(total_spend = sum(spend)) %>%
+  slice_max(total_spend, n = 20) %>% 
+  ggplot() +
+  geom_col(aes(x = reorder(country, total_spend), y = total_spend,
+               fill = country %in% c("USA")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Country",
+    y = "Total Spend (Million GBP)",
+    title = "International Tourism: Total Spend (2002-2009)",
+    subtitle = "Top 20")
+```
+
+### Spend per Visit by Country of Residence
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(country) %>% 
+  summarise(total_spend = sum(spend),
+            total_visits = sum(visits),
+            spend_per_visit = total_spend / total_visits) %>%
+  filter(total_visits > 500) %>%
+  ggplot() +
+  geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
+               fill = country %in% c("Australia", "China", "Canada", "Switzerland")),
+           show.legend = FALSE, colour = "white") +
+  scale_fill_manual(values = c("FALSE" = "grey60",
+                               "TRUE" = "#540453")) +
+  coord_flip() +
+  labs(
+    x = "Country",
+    y = "Total Spend (Million GBP) / Visit (Thousands)",
+    title = "International Tourism: Total Spend per Visit (2002-2009)",
+    subtitle = "Countries w/ Over 500 Thousand Total Visits")
+```
+
+### Group of High Value Countries
+
+```{r}
+international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  group_by(country) %>% 
+  summarise(total_spend = sum(spend),
+            total_visits = sum(visits),
+            spend_per_visit = total_spend / total_visits) %>%
+  filter(total_visits > 500) %>% 
+  ggplot(aes(x = total_visits, y = spend_per_visit)) +
+  geom_point(aes(colour = country %in% c("Australia", "China", "Canada", "Switzerland")), 
+             show.legend = FALSE,
+             size = 4) +
+  scale_colour_manual(values = c("FALSE" = "grey60",
+                                 "TRUE" = "#970061")) +
+  ggrepel::geom_text_repel(aes(x = total_visits, y = spend_per_visit, label = country)) +
+  labs(
+    x = "Visits (Thousands)",
+    y = "Total Spend (Million GBP) / Visit (Thousands)",
+    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
+    subtitle = "Countries w/ Over 500 Thousand Total Visits")
+```
+
+### By Region Visited
+
+"Information at the regional level is often based on very small sample sizes"  
+"The International Passenger Survey is a national survey, and is not designed to be statistically robust at the regional level."

### 2023-06-15 scripts/cleaning_script.R

@@ -13,8 +13,9 @@ regional_domestic_tourism <- read_csv("data/raw_data/regional_domestic_tourism.c
 
 local_authority_codes <- read_csv("data/raw_data/local_authority_codes.csv")
 
-international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv") %>%
-  clean_names()
+international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv")
+
+local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
 
 # demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
 #   clean_names()
@@ -139,6 +140,11 @@ international_visits <- read_csv("data/raw_data/international-passenger-survey-s
 #   rename(year = date_code) %>% 
 #   clean_names()
 
+# Clean International Tourism Data ------------------------------------------------------------
+
+international_visits_clean <- international_visits %>% 
+  clean_names()
+
 # Clean Regional Domestic Tourism Data ------------------------------------------------------------
 
 regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
@@ -176,7 +182,17 @@ regional_domestic_tourism_individual_clean <- regional_domestic_tourism %>%
   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
   clean_names() %>%
   rename(year = date_code) %>% 
-  inner_join(local_authority_codes, by = "feature_code") %>% 
+  inner_join(local_authority_codes, by = "feature_code")
+
+regional_domestic_tourism_non_gb_clean <- regional_domestic_tourism %>%
+  filter(feature_code != "S92000003",
+         region_of_residence != "All of GB") %>%
+  arrange(date_code) %>% 
+  select(-c(measurement, units)) %>% 
+  pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
+  clean_names() %>%
+  rename(year = date_code) %>% 
+  inner_join(local_authority_codes, by = "feature_code")
   
 regional_data_joined <- local_authority_geo %>% 
   left_join(regional_domestic_tourism_individual_clean, by = c("code" = "feature_code"))
@@ -265,6 +281,8 @@ regional_data_joined <- local_authority_geo %>%
 
[…]

### 2023-06-15 visit_scotland_notebook.Rmd
Added Canadian Case Study Hypothesis Test

@@
 "The International Passenger Survey is a national survey, and is not designed to be statistically robust at the regional level."
+
+### By Season
+
+```{r}
+international_visits %>%
+  filter(country == "Canada") %>% 
+  mutate(exp_per_visit = spend / visits,
+         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
+  summarise(mean_visits = mean(visits),
+            mean_exp = mean(spend),
+            mean_exp_per_visit = mean(exp_per_visit))
+```
+```{r}
+canada_sample <- international_visits %>%
+  filter(country == "Canada") %>% 
+  mutate(exp_per_visit = spend / visits,
+         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No"))
+```
+
+```{r}
+observed_stat <- canada_sample %>% 
+  specify(exp_per_visit ~ spring_summer) %>%
+  calculate(stat = "diff in means", order = c("Yes", "No"))
+
+observed_stat
+```
+
+```{r}
+null_distribution <- canada_sample %>% 
+  specify(response = exp_per_visit, explanatory = spring_summer) %>%
+  hypothesize(null = "independence") %>%
+  generate(reps = 1000, type = "permute") %>% 
+  calculate(stat = "diff in means", order = c("Yes", "No"))
+```
+
+```{r}
+null_distribution %>%
+  visualise() +
+  shade_p_value(obs_stat = observed_stat, direction = "both")
+```
+
+```{r}
+null_distribution %>%
+  get_p_value(obs_stat = observed_stat, direction = "both")
+```

### 2023-06-16 draft_work.Rmd
Minor Aesthetic Changes To A Range of Plots

@@
 -----------------------------------------------------------
+
+```{r}
+
+library(broom)
+library(factoextra)
+
+international_summary <- international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
+         !country %in% c("USA", "Germany")) %>% 
+  group_by(country) %>% 
+  summarise(total_spend = sum(spend),
+            total_visits = sum(visits),
+            spend_per_visit = total_spend / total_visits)
+  # filter(total_visits > 500,
+  #        spend_per_visit > 0.5)
+
+international_clust <- international_visits %>% 
+  select(-c(quarter, age, sample)) %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
+         !country %in% c("USA", "Germany")) %>% 
+  group_by(country) %>% 
+  summarise(total_spend = sum(spend),
+            total_visits = sum(visits),
+            spend_per_visit = total_spend / total_visits) %>% 
+  # filter(total_visits > 500,
+  #        spend_per_visit > 0.5) %>% 
+  select(total_visits, spend_per_visit)
+
+```
+
+```{r}
+
+k_clusters <- tibble(k = 1:63) %>% 
+  mutate(kclust = map(k, ~ kmeans(international_clust,
+                                  centers = .x,
+                                  nstart = 25)),
+         tidied = map(kclust, tidy),
+         glanced = map(kclust, glance),
+         augmented = map(kclust, augment, international_summary))
+
+# Unnest `glanced` to view `tot.withinss`
+clusterings <- k_clusters %>% 
+  unnest(glanced)
+
+clusterings
+```
+
+```{r}
+clusterings %>% 
+  ggplot(aes(x = k, y = tot.withinss)) +
+  geom_point() +
+  geom_line() +
+  scale_x_continuous(breaks = seq(1, 25, 1))
+```
+
+```{r}
+fviz_nbclust(international_clust,
+             kmeans,
+             method = "wss", #within sum of squares
+             nstart = 25)
+```
+
+```{r}
+fviz_nbclust(international_clust,
+             kmeans,
+             method = "silhouette",
+             nstart = 25)
+```
+
+```{r}
+clusterings %>% 
+  unnest(augmented) %>% # Unnest augmented created in step 5.1
+  filter(k == 2) %>% # Set number of clusters
+  ggplot(aes(x = total_visits, y = spend_per_visit, colour = .cluster)) +
+  geom_point()
+```
+
+```{r}
+clusterings %>% 
+  unnest(augmented) %>% # Unnest augmented created in step 5.1
+  filter(k == 4) %>% 
+  group_by(.cluster) %>% 
+  filter(.cluster == 2)
+```

### 2023-06-16 visit_scotland_notebook.Rmd
Minor Aesthetic Changes To A Range of Plots

@@
   ggplot(aes(x = date_code, y = visits)) +
-  geom_line(group = 1) +
-  geom_point(aes(colour = visits_change_label), 
-             show.legend = FALSE,
-             size = 4) +
+  geom_line(group = 1, size = 1, colour = "#540453") +
+  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
   labs(x = "\n Year Range",
@@
        title = "Average Annual Number of Domestic Vistors",
-       subtitle = "3 Year Average")
+       subtitle = "3 Year Average") +
+  ylim(0, 13000)
 
@@
   ggplot(aes(x = date_code, y = expenditure)) +
-  geom_line(group = 1) +
-  geom_point(aes(colour = exp_change_label), 
-             show.legend = FALSE,
-             size = 4) +
+  geom_line(group = 1, size = 1, colour = "#540453") +
+  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
   labs(x = "\n Year Range",
@@
        title = "Average Annual Expenditure of Domestic Vistors",
-       subtitle = "3 Year Average")
+       subtitle = "3 Year Average") +
+  ylim(0, 3500)
 
@@
   ggplot(aes(x = date_code, y = nights)) +
-  geom_line(group = 1) +
-  geom_point(aes(colour = nights_change_label), 
-             show.legend = FALSE,
-             size = 4) +
+  geom_line(group = 1, size = 1, colour = "#540453") +
+  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
   labs(x = "\n Year Range",
@@
   ggplot(aes(x = date_code, y = exp_per_visit)) +
-  geom_line(group = 1) +
-  geom_point(aes(colour = exp_per_visit_label), 
-             show.legend = FALSE,
-             size = 4) +
+  geom_line(group = 1, size = 1, colour = "#540453") +
+  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
   labs(x = "\n Year Range",
@@
 
-##### Plot
+##### Mean Spend Per Visit Plot
 

### 2023-06-16 visit_scotland_notebook.Rmd
Updated Summary Stats for Domestic and International

@@
 library(modelr)
+library(skimr)
 ```
@@
 
+## Annual Average Stats
+
+#### 5 Figure Summary
+
+```{r}
+regional_domestic_tourism_all %>% 
+  skim()
+```
+
+#### IQR
+
+```{r}
+regional_domestic_tourism_all %>% 
+  summarise(visits_iqr= IQR(visits),
+            expenditure_iqr= IQR(expenditure))
+```
+
+#### Median
+
+```{r}
+regional_domestic_tourism_all %>% 
+  summarise(median_visits = median(visits),
+            median_expenditure = median(expenditure))
+
+```
+
+### Annual Average Boxplots
+
+```{r}
+regional_domestic_tourism_all %>% 
+  ggplot(aes(x = visits, y = region_of_residence)) +
+  geom_boxplot(fill = "#540453", alpha = 0.5) +
+  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color = "#1d1d65", fill="#1d1d65") +
+  labs(
+    title = "Distribution of Annual Number of Domestic Vistors",
+    x = "Visits (Thousands)",
+    y = "Region of Residence",
+    subtitle = "3 Year Averages")
+```
+
+```{r}
+regional_domestic_tourism_all %>% 
+  ggplot(aes(x = expenditure, y = region_of_residence)) +
+  geom_boxplot(fill = "#1d1d65", alpha = 0.5) +
+  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color="#540453", fill="#540453") +
+  labs(
+    title = "Distribution of Average Annual Expenditure of Domestic Vistors",
+    x = "Expenditure (Million GBP)",
+    y = "Region of Residence",
+    subtitle = "3 Year Averages")
+```
+
 ## Trends Over Time
@@
        title = "Average Annual Number of Domestic Vistors",
-       subtitle = "3 Year Average") +
+       subtitle = "3 Year Averages") +
   ylim(0, 13000)
@@
        title = "Average Annual Expenditure of Domestic Vistors",
-       subtitle = "3 Year Average") +
+       subtitle = "3 Year Averages") +
   ylim(0, 3500)
@@
 
-### Visit Stats
+### Annual Average Stats
+
+#### Mean
 
@@
   group_by(year) %>% 
-  summarise(sum_annual_visits = sum(visits)) %>% 
-  summarise(avg_annual_visits = mean(sum_annual_visits))
-
+  summarise(sum_annual_visits = sum(visits),
+            sum_annual_spend = sum(spend)) %>%
+  summarise(mean_annual_visits = mean(sum_annual_visits),
+            mean_annual_spend = mean(sum_annual_spend))
 ```
@@
 ### Expenditure Stats
-
-```{r}
-international_visits %>%
-  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
-  group_by(year) %>% 
-  summarise(sum_annual_exp = sum(spend)) %>% 
-  summarise(avg_annual_spend = mean(sum_annual_exp))
-
-```
 

### 2023-06-16 draft_work.Rmd
Added Tourism Businesses Dataset / Tidied Cleaning Script

@@
 ---
+
+```{r}
+# Clean Activities Data ------------------------------------------------------------
+
+# activities_clean <- activities %>%
+#   filter(tourism_activity != "All") %>% 
+#   select(-c(measurement, units)) %>%
+#   arrange(date_code) %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits,
+#          tourism_activity = recode(tourism_activity,
+#                                    "Day out to a beauty/health centre/spa, etc." = "Beauty/Health Centre/Spa",
+#                                    "Day trips/excursions for other leisure purpose" = "Day Trips for Other Leisure Purpose",
+#                                    "Entertainment - to a cinema, concert or theatre	" = "Entertainment (eg. Cinema, Concert)",
+#                                    "General day out/ to explore an area" = "General Day Out / Explore an Area",
+#                                    "Leisure activities e.g. hobbies & evening classes" = "Leisure Activities (eg. Hobbies)",
+#                                    "Night out to a bar, pub and/or club" = "Night Out (eg. Bar, Pub)",
+#                                    "Outdoor leisure activities e.g. walking, golf" = "Outdoor Leisure (eg. Golf)",
+#                                    "Shopping for items that you do not regularly buy" = "Shopping for Non-Regular Purchases",
+#                                    "Special personal events e.g. wedding, graduation" = "Special Personal Event (eg. Wedding)",
+#                                    "Special public event e.g. festival, exhibition" = "Special Public Event (eg. Festival)",
+#                                    "Sport participation, e.g. exercise classes, gym" = "Sport Participation",
+#                                    "Visited friends or family for leisure	" = "Visiting Friends/Family for Leisure",
+#                                    "Visitor attraction e.g. theme park, museum, zoo" = "Visitor Attraction (eg. Museum)",
+#                                    "Watched live sporting events (not on TV)" = "Attending Sporting Event",
+#                                    "Went out for a meal" = "Eating Out")) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+
+# Clean Demographic Data ------------------------------------------------------------
+
+# all_demographics_clean <- demographics %>%
+#   filter(age == "All", marital_status == "All", gender == "All", employment_status == "All",
+#          children == "All",  access_to_car == "All", social_grade == "All") %>%
+#   select(-c(measurement, units)) %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits,
+#          exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
+#          visits_change_label = case_when(Visits > lag(Visits) ~ "Increased",
+#                                          Visits < lag(Visits) ~ "Decreased",
+#                                          Visits == lag(Visits) ~ "No Change",
+#                                          TRUE ~ "Starting Year"),
+#          exp_change_label = case_when(Expenditure > lag(Expenditure) ~ "Increased",
+#                                       Expenditure < lag(Expenditure) ~ "Decreased",
+#                                       Expenditure == lag(Expenditure) ~ "No Change",
+#                                       TRUE ~ "Starting Year"),
+#          exp_per_visit_label = case_when(exp_per_visit > lag(exp_per_visit) ~ "Increased",
+#                                          exp_per_visit < lag(exp_per_visit) ~ "Decreased",
+#                                          exp_per_visit == lag(exp_per_visit) ~ "No Change",
+#                                          TRUE ~ "Starting Year")) %>% 
+#   select(date_code, Visits, Expenditure, exp_per_visit, exp_per_visit_pct_change, 
+#          visits_change_label, exp_change_label, exp_per_visit_label) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# employment_demographics_clean <- demographics %>%
+#   select(-c(feature_code, age, marital_status, gender, children, access_to_car, 
+#             social_grade, measurement, units)) %>% 
+#   filter(employment_status != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, employment_status, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# gender_demographics_clean <- demographics %>%
+#   select(-c(feature_code, age, marital_status, children, access_to_car, 
+#             social_grade, measurement, units, employment_status)) %>% 
+#   filter(gender != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, gender, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# age_demographics_clean <- demographics %>%
+#   select(-c(feature_code, gender, marital_status, children, access_to_car, 
+#             social_grade, measurement, units, employment_status)) %>% 
+#   filter(age != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, age, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# marital_status_demographics_clean <- demographics %>%
+#   select(-c(feature_code, gender, age, children, access_to_car, 
+#             social_grade, measurement, units, employment_status)) %>% 
+#   filter(marital_status != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, marital_status, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# children_demographics_clean <- demographics %>%
+#   select(-c(feature_code, gender, age, marital_status, access_to_car, 
+#             social_grade, measurement, units, employment_status)) %>% 
+#   filter(children != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, children, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# car_demographics_clean <- demographics %>%
+#   select(-c(feature_code, gender, age, marital_status, children, 
+#             social_grade, measurement, units, employment_status)) %>% 
+#   filter(access_to_car != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, access_to_car, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+# 
+# social_demographics_clean <- demographics %>%
+#   select(-c(feature_code, gender, age, marital_status, children, 
+#             access_to_car, measurement, units, employment_status)) %>% 
+#   filter(social_grade != "All") %>% 
+#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
+#   arrange(date_code, social_grade) %>% 
+#   mutate(exp_per_visit = Expenditure / Visits) %>% 
+#   select(date_code, social_grade, Visits, Expenditure, exp_per_visit) %>% 
+#   rename(year = date_code) %>% 
+#   clean_names()
+```
+
+```{r}
+tourism_businesses %>%
+  filter(local_authority != "Scotland",
+         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(local_authority) %>% 
+  summarise(mean_gva = mean(gva),
+            total_gva = sum(gva)) %>% 
+  arrange(desc(mean_gva))
+
+```
+
+```{r}
+tourism_businesses %>%
+  filter(local_authority == "Scotland",
+         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(local_authority) %>% 
+  summarise(mean_gva = mean(gva),
+            total_gva = sum(gva))
+```
 

### 2023-06-16 visit_scotland_notebook.Rmd
Added Tourism Businesses Dataset / Tidied Cleaning Script

@@
 international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
+tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
@@
   select(-c(quarter, age, sample)) %>%
-  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
+         purpose == "Holiday") %>% 
   group_by(country) %>% 
@@
     title = "International Tourism: Total Visits (2002-2009)",
-    subtitle = "Top 20")
+    subtitle = "Top 20 (Holiday Only)")
 ```
@@
     title = "International Tourism: Total Spend (2002-2009)",
-    subtitle = "Top 20")
+    subtitle = "Top 20 (Holiday Only)")
 ```
@@
   geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
-               fill = country %in% c("Australia", "China", "Canada", "Switzerland")),
+               fill = country %in% c("Australia", "China", "Canada")),
            show.legend = FALSE, colour = "white") +
@@
     title = "International Tourism: Total Spend per Visit (2002-2009)",
-    subtitle = "Countries w/ Over 500 Thousand Total Visits")
+    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)")
 ```
@@
   ggplot(aes(x = total_visits, y = spend_per_visit)) +
-  geom_point(aes(colour = country %in% c("Australia", "China", "Canada", "Switzerland")), 
+  geom_point(aes(colour = country %in% c("Australia", "China", "Canada")), 
              show.legend = FALSE,
@@
     title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
-    subtitle = "Countries w/ Over 500 Thousand Total Visits")
+    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)")
 ```
@@
 international_visits %>%
-  filter(country == "Canada") %>% 
+  filter(country == "Canada",
+         purpose == "Holiday") %>% 
   mutate(exp_per_visit = spend / visits,
@@
 canada_sample <- international_visits %>%
-  filter(country == "Canada") %>% 
+  filter(country == "Canada",
+         purpose == "Holiday") %>% 
   mutate(exp_per_visit = spend / visits,

### 2023-06-16 scripts/cleaning_script.R

@@ -17,132 +17,17 @@ international_visits <- read_csv("data/raw_data/international-passenger-survey-s
 
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
 
-# demographics <- read_csv("data/raw_data/tourism_day_visits_demographics.csv") %>% 
-#   clean_names()
+tourism_businesses <- read_csv(here("data/raw_data/tourism-businesses-in-scotland.csv")) %>% clean_names()
 
-# activities <- read_csv("data/raw_data/tourism_day_visits_activities.csv") %>%
-#   clean_names()
+# Clean Tourism Business Data ------------------------------------------------------------
 
-# domestic_day_visits <- read_excel("data/raw_data/gbdvs-2019-scotland-and-gb.xlsx") %>% 
-#   clean_names()
-
-# location <- read_csv("data/raw_data/tourism_day_visits_location.csv") %>% 
-#   clean_names()
-# 
-# transport <- read_csv("data/raw_data/tourism_day_visits_transport.csv") %>% 
-#   clean_names()
-# 
-# accomodation_occupancy <- read_csv("data/raw_data/scottish_accomodation_occupancy.csv") %>% 
-#   clean_names()
-# 
-
-# Clean Demographic Data ------------------------------------------------------------
-
-# all_demographics_clean <- demographics %>%
-#   filter(age == "All", marital_status == "All", gender == "All", employment_status == "All",
-#          children == "All",  access_to_car == "All", social_grade == "All") %>%
-#   select(-c(measurement, units)) %>% 
-#   pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>%
-#   arrange(date_code) %>% 
-#   mutate(exp_per_visit = Expenditure / Visits,
-#          exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
-#          visits_change_label = case_when(Visits > lag(Visits) ~ "Increased",
-#                                          Visits < lag(Visits) ~ "Decreased",
-#                                          Visits == lag(Visits) ~ "No Change",
-#                                          TRUE ~ "Starting Year"),
-#          exp_change_label = case_when(Expenditure > lag(Expenditure) ~ "Increased",
-#                                       Expenditure < lag(Expenditure) ~ "Decreased",
-#                                       Expenditure == lag(Expenditure) ~ "No Change",
[…]

### 2023-06-17 visit_scotland_notebook.Rmd
Updated Visualisation Aesthetics / Added Template for README.md

@@
 
-### Annual Average Boxplots
-
-```{r}
-regional_domestic_tourism_all %>% 
-  ggplot(aes(x = visits, y = region_of_residence)) +
-  geom_boxplot(fill = "#540453", alpha = 0.5) +
-  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color = "#1d1d65", fill="#1d1d65") +
-  labs(
-    title = "Distribution of Annual Number of Domestic Vistors",
-    x = "Visits (Thousands)",
-    y = "Region of Residence",
-    subtitle = "3 Year Averages")
-```
-
-```{r}
-regional_domestic_tourism_all %>% 
-  ggplot(aes(x = expenditure, y = region_of_residence)) +
-  geom_boxplot(fill = "#1d1d65", alpha = 0.5) +
-  stat_summary(fun.y = mean, geom = "point", shape = 4, size = 5, color="#540453", fill="#540453") +
-  labs(
-    title = "Distribution of Average Annual Expenditure of Domestic Vistors",
-    x = "Expenditure (Million GBP)",
-    y = "Region of Residence",
-    subtitle = "3 Year Averages")
-```
-
 ## Trends Over Time
@@
 
-```
-### Domestic Tourism / Nights Stayed
-
-```{r}
-
-regional_domestic_tourism_all %>%
-  ggplot(aes(x = date_code, y = nights)) +
-  geom_line(group = 1, size = 1, colour = "#540453") +
-  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
-  labs(x = "\n Year Range",
-       y = "Nights (Thousands) \n",
-       title = "Average Annual Nights Stayed by Domestic Vistors",
-       subtitle = "3 Year Average")
-
-```
-
-### Domestic Tourism / Expenditure per Visit
-
-```{r}
-regional_domestic_tourism_all %>%
-  ggplot(aes(x = date_code, y = exp_per_visit)) +
-  geom_line(group = 1, size = 1, colour = "#540453") +
-  geom_point(colour = "#970061", show.legend = FALSE, size = 4) +
-  labs(x = "\n Year Range",
-       y = "3x Year Average Expenditure per Visit (Thousands) \n",
-       title = "Average Expenditure Per Visit Domestic Vistors",
-       subtitle = "3 Year Average")
 ```
@@
 
+```
+
+#### Gross Value Added
+
+```{r}
+tourism_businesses %>%
+  filter(local_authority != "Scotland",
+         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(local_authority) %>% 
+  summarise(total_gva = sum(gva)) %>% 
+  slice_max(total_gva, n = 5)
+
+tourism_businesses %>%
+  filter(local_authority %in% c("City of Edinburgh", "Glasgow City", "Aberdeen City",
+                                "Highland", "Fife"),
+         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  ggplot() +
+  geom_boxplot(aes(x = gva, y = local_authority, fill = local_authority), 
+               alpha = 0.8,
+               show.legend = FALSE) +
+  scale_fill_manual(values = c("#540453", "#970061", "#1d1d65", "#b6cb2b", "#9fd6f3")) +
+  scale_colour_manual(values = c("#540453", "#970061", "#1d1d65", "#b6cb2b", "#9fd6f3")) +
+  labs(
+    x = "Gross Value Added (Million GBP)",
+    y = "Local Authority",
+    title = "Distribution of Annual Gross Value Added",
+    subtitle = "Top 5 Regions: 2009-2019"
+  )
 ```

### 2023-06-17 visit_scotland_analysis.Rmd
Added Colour Scheme Object / File Renaming

---
title: "Visit Scotland Analysis"
output: html_notebook
---

## Setup

### Load Libraries

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
library(skimr)
```

### Run Cleaning Script & Read In Clean Data

```{r}
source(here("scripts/cleaning_script.R"))

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
```

### Set Colour Scheme for Visualisations

```{r}
colour_scheme <- c("#540453", "#1d1d65", "#970061", "#b6cb2b", "#9fd6f3")
```

## Annual Average Stats

#### 5 Figure Summary

```{r}
regional_domestic_tourism_all %>% 
  skim()
```

#### IQR

```{r}
regional_domestic_tourism_all %>% 
  summarise(visits_iqr= IQR(visits),
            expenditure_iqr= IQR(expenditure))
```

#### Median

```{r}
regional_domestic_tourism_all %>% 
  summarise(median_visits = median(visits),
            median_expenditure = median(expenditure))

```

## Trends Over Time

### Domestic Tourism / Visits

```{r}

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = visits)) +
  geom_line(group = 1, size = 2, colour = colour_scheme[1]) +
  geom_point(colour = colour_scheme[3], show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Visitors (Thousands) \n",
       title = "Average Annual Number of Domestic Vistors",
       subtitle = "3 Year Averages") +
  ylim(0, 13000) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

```

### Domestic Tourism / Expenditure

```{r}

regional_domestic_tourism_all %>%
  ggplot(aes(x = date_code, y = expenditure)) +
  geom_line(group = 1, size = 2, colour = colour_scheme[1]) +
  geom_point(colour = colour_scheme[3], show.legend = FALSE, size = 4) +
  labs(x = "\n Year Range",
       y = "Expenditure (Million GBP) \n",
       title = "Average Annual Expenditure of Domestic Vistors",
       subtitle = "3 Year Averages") +
  ylim(0, 3500) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

```

## Domestic Tourism

#### Average Visits By Region

```{r}

regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_visits = mean(visits)) %>% 
  ggplot(aes(fill = mean_visits)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Number of Domestic Vistors",
    subtitle = "By Region",
    fill = "Visits (Thousands)") +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

```

#### Expenditure by Region

```{r}
regional_data_joined %>% 
  group_by(code) %>% 
  summarise(mean_exp = mean(expenditure)) %>% 
  ggplot(aes(fill = mean_exp)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Average Annual Expenditure of Domestic Vistors",
    subtitle = "By Region",
    fill = "Expenditure (Million GBP)") +
    theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```

#### Spend Per Visit

##### Mean Spend Per Visit Plot

```{r}
regional_domestic_tourism_individual %>%
  filter(visits != 0,
         expenditure != 0) %>% 
  mutate(exp_per_visit = expenditure / visits, rm.na = TRUE) %>%
  group_by(local_authority) %>% 
  summarise(mean_exp_per_visit = mean(exp_per_visit)) %>% 
  arrange(desc(mean_exp_per_visit)) %>%
  ggplot() +
  geom_col(aes(x = reorder(local_authority, mean_exp_per_visit), y = mean_exp_per_visit,
               fill = local_authority %in% c("City of Edinburgh", "Glasgow City", "Highland")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey80",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Region",
    y = "Mean Expenditure per Visit (Million GBP / Thousand Visits)",
    title = "Domestic Tourism Mean Expenditure per Visit") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

#### Nights Stayed

##### Plot

```{r}
regional_domestic_tourism_individual %>% 
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot() +
  geom_col(aes(x = reorder(local_authority, mean_nights_per_visit), y = mean_nights_per_visit,
               fill = local_authority %in% c("Shetland Islands", "Orkney Islands", "Na h-Eileanan Siar",
                                             "City of Edinburgh", "Glasgow City")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey80",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Region",
    y = "Avg. Nights per Visit",
    title = "Domestic Tourism Avg. Nights per Visit") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

##### Map

```{r}
regional_data_joined %>%
  mutate(nights_per_visit = nights / visits) %>% 
  group_by(local_authority) %>% 
  summarise(mean_nights_per_visit = mean(nights_per_visit, na.rm = TRUE)) %>%
  ggplot(aes(fill = mean_nights_per_visit)) + 
  geom_sf(colour = "grey90", size = 0.1) +
  labs(
    x = "Longitude",
    y = "Latitude",
    title = "Domestic Tourism Mean Nights per Visit",
    fill = "Mean Nights per Visit"
  ) +
  theme(panel.background = element_rect(fill = "white"),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks = element_blank(),
        rect = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(size = 15, face = "bold"))

```

#### Gross Value Added

```{r}
tourism_businesses %>%
  filter(local_authority != "Scotland",
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  group_by(local_authority) %>% 
  summarise(total_gva = sum(gva)) %>% 
  slice_max(total_gva, n = 5)

tourism_businesses %>%
  filter(local_authority %in% c("City of Edinburgh", "Glasgow City", "Aberdeen City",
                                "Highland", "Fife"),
         year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
  ggplot() +
  geom_boxplot(aes(x = gva, y = local_authority, fill = local_authority), 
               alpha = 0.8,
               show.legend = FALSE) +
  scale_fill_manual(values = colour_scheme) +
  scale_colour_manual(values = colour_scheme) +
  labs(
    x = "Gross Value Added (Million GBP)",
    y = "Local Authority",
    title = "Distribution of Annual Gross Value Added",
    subtitle = "Top 5 Regions: 2009-2019"
  ) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))
```

#### Marketing Edinburgh to Domestic Tourists: Mini Case Study

##### Visits by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>% 
  ggplot(aes(x = visits, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Annual Visits by Country of Residence",
    subtitle = "Edinburgh",
    x = "Visits (Thousands)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```

##### Spend Per Visit by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>%
  mutate(exp_per_visit = expenditure / visits) %>% 
  ggplot(aes(x = exp_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Expenditure per Visit by Country of Residence",
    subtitle = "Edinburgh",
    x = "Expenditure per Visit (Million GBP / Thousand Visits)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```

##### Nights by Country of Residence

```{r}
regional_domestic_tourism_non_gb_clean %>%
  filter(local_authority %in% c("City of Edinburgh")) %>% 
  mutate(nights_per_visit = nights / visits) %>%
  ggplot(aes(x = nights_per_visit, y = region_of_residence, fill = region_of_residence == "Scotland")) +
  geom_density_ridges(show.legend = FALSE, alpha = 0.5) +
  theme_ridges() +
  theme(axis.title.y = element_blank()) +
  scale_fill_manual(values = c("FALSE" = colour_scheme[2],
                               "TRUE" = colour_scheme[1])) +
  labs(
    title = "Distribution of Nights by Country of Residence",
    subtitle = "Edinburgh",
    x = "Nights") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 13),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"),
        axis.text.y = element_text(face = "bold"))
```

##### Linear Model: Predict Spend by Visits & Nights?

```{r}
regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England") %>% 
  summarise(cor(expenditure, visits))
```

```{r}
regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England") %>% 
  summarise(cor(expenditure, nights))
```

```{r}
edinburgh_england <- regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England")
```

```{r}
model_edinburgh <- lm(formula = expenditure ~ visits, data = edinburgh_england)
summary(model_edinburgh)
```

```{r}
edinburgh_england %>%
  add_predictions(model_edinburgh) %>%
  add_residuals(model_edinburgh) %>% 
  ggplot(aes(x = visits, y = expenditure)) +
  geom_point() +
  geom_line(aes(y = pred), col = colour_scheme[3], size = 1) +
  labs(
    x = "Visits (Thousands)",
    y = "Expenditure (Million GBP)",
    title = "English Based Visitors To Edinburgh: Expenditure / Visits",
    subtitle = "Based On 3 Year Annual Averages Between 2009-2019")
```
Model: spend ~ visits

Interpretation: ~97% of the variation in expenditure can be explained by the number of visits.

Question: The largest increase in visitor numbers is from 2009-2011 Avg. to 2010-2012 Avg. ~6%. If this percentage increase in visits was replicated in based on the most recent set of figures resulting in ~1803 (Thousand) visitors - what would the model predict for expenditure?

Answer: If visits were increased as above, the model would predict expenditure of ~632 Million GBP (Low Estimate ~620, High Estimate ~644)

As calculated below.

Step 1.
outcome = b0 + b1 * 1st Predictor

Step 2.
expenditure = b0(intercept) + b1(coefficient) * 1st Predictor

Step 3.
expenditure = b0(intercept) + b1(coefficient) * `visits`

Step 4.
expenditure = -493.61749 + 0.62423 * `1803`

Step 5.
expenditure = ~632 (Low Estimate ~620, High Estimate ~644)

```{r}
632 + c(-12.34, 12.34)
```

## International Tourism

### Annual Average Stats

#### Mean

```{r}
international_visits %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
  group_by(year) %>% 
  summarise(sum_annual_visits = sum(visits),
            sum_annual_spend = sum(spend)) %>%
  summarise(mean_annual_visits = mean(sum_annual_visits),
            mean_annual_spend = mean(sum_annual_spend))
```

### Expenditure Stats

### Visitors by Country of Residence

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_visits = sum(visits)) %>%
  slice_max(total_visits, n = 20) %>% 
  ggplot(aes(x = reorder(country, total_visits), y = total_visits)) +
  geom_col(aes(x = reorder(country, total_visits), y = total_visits,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Visits (Thousands)",
    title = "International Tourism: Total Visits (2002-2009)",
    subtitle = "Top 20 (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

### Spend by Country of Residence

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend)) %>%
  slice_max(total_spend, n = 20) %>% 
  ggplot() +
  geom_col(aes(x = reorder(country, total_spend), y = total_spend,
               fill = country %in% c("USA")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP)",
    title = "International Tourism: Total Spend (2002-2009)",
    subtitle = "Top 20 (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

### Spend per Visit by Country of Residence

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>%
  ggplot() +
  geom_col(aes(x = reorder(country, spend_per_visit), y = spend_per_visit,
               fill = country %in% c("Australia", "China", "Canada")),
           show.legend = FALSE, colour = "white") +
  scale_fill_manual(values = c("FALSE" = "grey60",
                               "TRUE" = colour_scheme[1])) +
  coord_flip() +
  labs(
    x = "Country",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Total Spend per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "blank"))
```

### Group of High Value Countries

```{r}
international_visits %>% 
  select(-c(quarter, age, sample)) %>%
  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019),
         purpose == "Holiday") %>% 
  group_by(country) %>% 
  summarise(total_spend = sum(spend),
            total_visits = sum(visits),
            spend_per_visit = total_spend / total_visits) %>%
  filter(total_visits > 500) %>% 
  ggplot(aes(x = total_visits, y = spend_per_visit)) +
  geom_point(aes(colour = country %in% c("Australia", "China", "Canada")), 
             show.legend = FALSE,
             size = 4) +
  scale_colour_manual(values = c("FALSE" = "grey60",
                                 "TRUE" = colour_scheme[3])) +
  ggrepel::geom_text_repel(aes(x = total_visits, y = spend_per_visit, label = country)) +
  labs(
    x = "Visits (Thousands)",
    y = "Total Spend (Million GBP) / Visit (Thousands)",
    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
    subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", linetype = "dashed"))
```

### By Region Visited

"Information at the regional level is often based on very small sample sizes"  
"The International Passenger Survey is a national survey, and is not designed to be statistically robust at the regional level."

### By Season

```{r}
international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
  summarise(mean_visits = mean(visits),
            mean_exp = mean(spend),
            mean_exp_per_visit = mean(exp_per_visit))
```
```{r}
canada_sample <- international_visits %>%
  filter(country == "Canada",
         purpose == "Holiday") %>% 
  mutate(exp_per_visit = spend / visits,
         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No"))
```

```{r}
observed_stat <- canada_sample %>% 
  specify(exp_per_visit ~ spring_summer) %>%
  calculate(stat = "diff in means", order = c("Yes", "No"))

observed_stat
```

```{r}
null_distribution <- canada_sample %>% 
  specify(response = exp_per_visit, explanatory = spring_summer) %>%
  hypothesize(null = "independence") %>%
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("Yes", "No"))
```

```{r}
null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "both")
```

```{r}
null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "both")
```

### 2023-06-17 scripts/cleaning_script.R

@@ -4,7 +4,6 @@
 library(tidyverse)
 library(janitor)
 library(here)
-library(readxl)
 
 # Read In Raw Data ------------------------------------------------------------
 
@@ -41,15 +40,14 @@ regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
   clean_names() %>% 
   mutate(exp_per_visit = expenditure / visits,
          exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
-         nights_change_label = case_when(nights > lag(nights) ~ "Increased",
-                                         nights < lag(nights) ~ "Decreased",
-                                         nights == lag(nights) ~ "No Change",
-                                         TRUE ~ "Starting Year"),
+         visit_pct_change = (visits - lag(visits)) / lag(visits) * 100,
+         exp_pct_change = (expenditure - lag(expenditure)) / lag(expenditure) * 100,
+  
          visits_change_label = case_when(visits > lag(visits) ~ "Increased",
                                          visits < lag(visits) ~ "Decreased",
                                          visits == lag(visits) ~ "No Change",
                                          TRUE ~ "Starting Year"),
-         exp_change_label = case_when(expenditure > lag(expenditure) ~ "Increased",
+         exp_pct_change_label = case_when(expenditure > lag(expenditure) ~ "Increased",
                                       expenditure < lag(expenditure) ~ "Decreased",
                                       expenditure == lag(expenditure) ~ "No Change",
                                       TRUE ~ "Starting Year"),
@@ -57,7 +55,6 @@ regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
                                          exp_per_visit < lag(exp_per_visit) ~ "Decreased",
                                          exp_per_visit == lag(exp_per_visit) ~ "No Change",
                                          TRUE ~ "Starting Year"))
-
 
 regional_domestic_tourism_individual_clean <- regional_domestic_tourism %>%
   filter(feature_code != "S92000003",

### 2023-06-18 visit_scotland_analysis.Rmd
Added International Figures To Trends Over Time

@@
 
-### Run Cleaning Script & Read In Clean Data
+### Run Cleaning Script, Read In Clean Data & Set Colour Scheme for Visualisations
 
@@
 tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
+dom_int_summary <- read_csv(here("data/clean_data/dom_int_summary_clean.csv"))
+# international_visits_annual_summary <- read_csv(here("data/clean_data/international_visits_annual_summary_clean.csv"))
+# domestic_annual <- read_csv(here("data/clean_data/domestic_annual_clean.csv"))
+
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
-```
 
-### Set Colour Scheme for Visualisations
-
-```{r}
 colour_scheme <- c("#540453", "#1d1d65", "#970061", "#b6cb2b", "#9fd6f3")
@@
 
+### Domestic
+
 #### 5 Figure Summary
@@
 ```{r}
-regional_domestic_tourism_all %>% 
+dom_int_summary %>%
+  filter(dom_int == "Domestic") %>% 
+  skim()
+```
+
+```{r}
+dom_int_summary %>%
+  filter(dom_int == "International") %>% 
   skim()
@@
 ```{r}
-regional_domestic_tourism_all %>% 
+dom_int_summary %>%
+  filter(dom_int == "Domestic") %>%  
   summarise(visits_iqr= IQR(visits),
-            expenditure_iqr= IQR(expenditure))
+            expenditure_iqr= IQR(spend))
+```
+
+```{r}
+dom_int_summary %>%
+  filter(dom_int == "International") %>%  
+  summarise(visits_iqr= IQR(visits),
+            expenditure_iqr= IQR(spend))
 ```
@@
 ```{r}
-regional_domestic_tourism_all %>% 
+dom_int_summary %>%
+  filter(dom_int == "Domestic") %>%  
   summarise(median_visits = median(visits),
-            median_expenditure = median(expenditure))
+            median_spend = median(spend))
 
+```
+
+```{r}
+dom_int_summary %>%
+  filter(dom_int == "International") %>%  
+  summarise(median_visits = median(visits),
+            median_spend = median(spend))
 ```
@@
 
-### Domestic Tourism / Visits
+### Over Time / Visits
 
@@
 
-regional_domestic_tourism_all %>%
-  ggplot(aes(x = date_code, y = visits)) +
-  geom_line(group = 1, size = 2, colour = colour_scheme[1]) +
-  geom_point(colour = colour_scheme[3], show.legend = FALSE, size = 4) +
-  labs(x = "\n Year Range",
+dom_int_summary %>% 
+  ggplot() +
+  geom_line(aes(x = year, y = visits, colour = dom_int),
+          size = 2) +
+  geom_point(aes(x = year, y = visits, colour = dom_int), 
+             size = 4) +
+  ylim(0, 15000) +
+  labs(x = "\n Year",
        y = "Visitors (Thousands) \n",
-       title = "Average Annual Number of Domestic Vistors",
-       subtitle = "3 Year Averages") +
-  ylim(0, 13000) +
+       title = "Annual Visits",
+       subtitle = "Domestic & International Overnight Vistors",
+       colour = "") +
+  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
+  scale_colour_manual(values = c("Domestic" = "#540453",
+                                 "International" = "#9fd6f3")) +
   theme(plot.title = element_text(size = 15, face = "bold"),
@@
 
-### Domestic Tourism / Expenditure
+### Over Time / Spend
 
@@
 
-regional_domestic_tourism_all %>%
-  ggplot(aes(x = date_code, y = expenditure)) +
-  geom_line(group = 1, size = 2, colour = colour_scheme[1]) +
-  geom_point(colour = colour_scheme[3], show.legend = FALSE, size = 4) +
-  labs(x = "\n Year Range",
+dom_int_summary %>% 
+  ggplot() +
+  geom_line(aes(x = year, y = spend, colour = dom_int),
+          size = 2) +
+  geom_point(aes(x = year, y = spend, colour = dom_int), 
+             size = 4) +
+  ylim(0, 4000) +
+  labs(x = "\n Year",
        y = "Expenditure (Million GBP) \n",
-       title = "Average Annual Expenditure of Domestic Vistors",
-       subtitle = "3 Year Averages") +
-  ylim(0, 3500) +
+       title = "Annual Expenditure",
+       subtitle = "Domestic & International Overnight Vistors",
+       colour = "") +
+  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
+  scale_colour_manual(values = c("Domestic" = "#540453",
+                                 "International" = "#9fd6f3")) +
   theme(plot.title = element_text(size = 15, face = "bold"),
@@
                fill = local_authority %in% c("Shetland Islands", "Orkney Islands", "Na h-Eileanan Siar",
-                                             "City of Edinburgh", "Glasgow City")),
+                                             "City of Edinburgh", "Glasgow City", "Highland")),
            show.legend = FALSE, colour = "white") +
@@
 
-### Annual Average Stats
-
-#### Mean
-
-```{r}
-international_visits %>%
-  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>% 
-  group_by(year) %>% 
-  summarise(sum_annual_visits = sum(visits),
-            sum_annual_spend = sum(spend)) %>%
-  summarise(mean_annual_visits = mean(sum_annual_visits),
-            mean_annual_spend = mean(sum_annual_spend))
-```
-
-### Expenditure Stats
-
-### Visitors by Country of Residence
+### Total Visitors by Country of Residence
 
@@
   coord_flip() +
+  ylim(0, 3200) +
   labs(
@@
 
-### Spend by Country of Residence
+### Total Spend by Country of Residence
 
@@
 
+#### Bar Plot
+
 ```{r}
@@
 
-### Group of High Value Countries
+#### Scatter Plot
 
@@
 
-### By Region Visited
+### Marketing Scotland To Canadian Based Tourists
 
-"Information at the regional level is often based on very small sample sizes"  
-"The International Passenger Survey is a national survey, and is not designed to be statistically robust at the regional level."
-
-### By Season
+$H_0$: $\mu_{\textrm{spend per visit(Q1+Q4)}} - \mu_{\textrm{spend per visit(Q2+Q3)}} = 0$
+$H_a$: $\mu_{\textrm{spend per visit(Q1+Q4)}} - \mu_{\textrm{spend per visit(Q2+Q3)}} != 0$
 

### 2023-06-18 scripts/cleaning_script.R

@@ -29,6 +29,26 @@ tourism_businesses_clean <- tourism_businesses %>%
 international_visits_clean <- international_visits %>%
   clean_names()
 
+international_visits_annual_summary_clean <- international_visits_clean %>%
+  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
+  group_by(year) %>%
+  summarise(visits = sum(visits),
+            spend = sum(spend),
+            nights = sum(nights)) %>% 
+  mutate(dom_int = "International")
+
+
+# Clean Domestic Tourism Data ------------------------------------------------------------
+
+domestic_annual_clean <- read_csv("data/raw_data/gbts_scotland_annual.csv") %>% 
+  mutate(dom_int = "Domestic", .after = year)
+
+# Join Domestic And International Tourism Summaries ------------------------------------------------------------
+
+
+dom_int_summary <- bind_rows(domestic_annual_clean, international_visits_annual_summary_clean) %>% 
+  select(-nights)
+
 # Clean Regional Domestic Tourism Data ------------------------------------------------------------
 
 regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
@@ -86,6 +106,9 @@ write_csv(regional_domestic_tourism_individual_clean, here("data/clean_data/regi
 write_csv(regional_domestic_tourism_non_gb_clean, here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
 write_csv(international_visits_clean, here("data/clean_data/international_visits_clean.csv"))
 write_csv(tourism_businesses_clean, here("data/clean_data/tourism_businesses_clean.csv"))
+write_csv(dom_int_summary, here("data/clean_data/dom_int_summary_clean.csv"))
+# write_csv(domestic_annual_clean, here("data/clean_data/domestic_annual_clean.csv"))
+# write_csv(international_visits_annual_summary_clean, here("data/clean_data/international_visits_annual_summary_clean.csv"))
 
 # Remove Objects from Environment -----------------------------------------------------------
 
@@ -99,3 +122,6 @@ rm(international_visits)
 rm(local_authority_geo)
 rm(tourism_businesses)
 rm(tourism_businesses_clean)
+rm(domestic_annual_clean)
+rm(international_visits_annual_summary_clean)
+rm(dom_int_summary_clean)

### 2023-06-18 visit_scotland_analysis.Rmd
Added Regional Comparison Based On Country of Residence

@@
                                   linetype = "dashed"))
+```
+
+#### Scottish Based Tourism Compared To English Based Tourism
+
+```{r}
+regional_data_joined_sco_eng %>% 
+  filter(region_of_residence == "Scotland") %>%
+  group_by(local_authority) %>%
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot(aes(fill = mean_visits)) + 
+  geom_sf(colour = "grey90", size = 0.1) +
+  labs(
+    x = "Longitude",
+    y = "Latitude",
+    title = "Average Annual Number of Scottish Based Vistors",
+    subtitle = "By Region",
+    fill = "Visits (Thousands)") +
+  theme(panel.background = element_rect(fill = "white"),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        rect = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
+```
+
+```{r}
+regional_data_joined_sco_eng %>% 
+  filter(region_of_residence == "England") %>% 
+  group_by(local_authority) %>%
+  summarise(mean_visits = mean(visits)) %>% 
+  ggplot(aes(fill = mean_visits)) + 
+  geom_sf(colour = "grey90", size = 0.1) +
+  labs(
+    x = "Longitude",
+    y = "Latitude",
+    title = "Average Annual Number of English Based Vistors",
+    subtitle = "By Region",
+    fill = "Visits (Thousands)") +
+  theme(panel.background = element_rect(fill = "white"),
+        axis.text.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks = element_blank(),
+        rect = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank())
 ```

### 2023-06-18 scripts/cleaning_script.R

@@ -45,7 +45,6 @@ domestic_annual_clean <- read_csv("data/raw_data/gbts_scotland_annual.csv") %>%
 
 # Join Domestic And International Tourism Summaries ------------------------------------------------------------
 
-
 dom_int_summary <- bind_rows(domestic_annual_clean, international_visits_annual_summary_clean) %>% 
   select(-nights)
 
@@ -98,6 +97,9 @@ regional_domestic_tourism_non_gb_clean <- regional_domestic_tourism %>%
   
 regional_data_joined <- local_authority_geo %>% 
   left_join(regional_domestic_tourism_individual_clean, by = c("code" = "feature_code"))
+
+regional_data_joined_sco_eng <- local_authority_geo %>% 
+  left_join(regional_domestic_tourism_non_gb_clean, by = c("code" = "feature_code"))
 
 # Write Clean Data To .CSV -----------------------------------------------------------
 

### 2023-06-19 visit_scotland_analysis.Rmd
Added Diagnostic Tests for Linear Model / Removed Unused Data from Cleaning Script

@@
 library(skimr)
+library(ggfortify)
 ```
@@
 
-regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
 regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
@@
 dom_int_summary <- read_csv(here("data/clean_data/dom_int_summary_clean.csv"))
-# international_visits_annual_summary <- read_csv(here("data/clean_data/international_visits_annual_summary_clean.csv"))
-# domestic_annual <- read_csv(here("data/clean_data/domestic_annual_clean.csv"))
 
@@
 
-##### Linear Model: Predict Spend by Visits & Nights?
+##### Linear Model: Predict Spend by Visits
 
@@
   summarise(cor(expenditure, visits))
-```
-
-```{r}
-regional_domestic_tourism_non_gb_clean %>% 
-  filter(local_authority == "City of Edinburgh",
-         region_of_residence == "England") %>% 
-  summarise(cor(expenditure, nights))
 ```
@@
 ```
+
+```{r}
+autoplot(model_edinburgh)
+```
+
+- Residuals vs. Fitted (Tests Independence of Residuals): No strong evidence of a pattern. 
+- Normal Q-Q (Tests Normality of Residuals): Distribution of standardised residuals appears fairly normal. 
+- Scale-Location (Tests Constancy of Variation of Residuals): No strong evidence of funneling.
 

### 2023-06-19 scripts/cleaning_script.R

@@ -18,62 +18,12 @@ local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
 
 tourism_businesses <- read_csv(here("data/raw_data/tourism-businesses-in-scotland.csv")) %>% clean_names()
 
-# Clean Tourism Business Data ------------------------------------------------------------
-
-tourism_businesses_clean <- tourism_businesses %>%
-  clean_names() %>% 
-  select(-x7)
-
-# Clean International Tourism Data ------------------------------------------------------------
-
-international_visits_clean <- international_visits %>%
-  clean_names()
-
-international_visits_annual_summary_clean <- international_visits_clean %>%
-  filter(year %in% c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) %>%
-  group_by(year) %>%
-  summarise(visits = sum(visits),
-            spend = sum(spend),
-            nights = sum(nights)) %>% 
-  mutate(dom_int = "International")
-
-
-# Clean Domestic Tourism Data ------------------------------------------------------------
+# Domestic Tourism Data ------------------------------------------------------------
 
 domestic_annual_clean <- read_csv("data/raw_data/gbts_scotland_annual.csv") %>% 
   mutate(dom_int = "Domestic", .after = year)
 
-# Join Domestic And International Tourism Summaries ------------------------------------------------------------
-
-dom_int_summary <- bind_rows(domestic_annual_clean, international_visits_annual_summary_clean) %>% 
-  select(-nights)
-
-# Clean Regional Domestic Tourism Data ------------------------------------------------------------
-
-regional_domestic_tourism_all_clean <- regional_domestic_tourism %>%
-  filter(feature_code == "S92000003",
-         region_of_residence == "All of GB") %>%
-  arrange(date_code) %>% 
-  select(-c(measurement, units)) %>% 
-  pivot_wider(names_from = breakdown_of_domestic_tourism, values_from = value) %>% 
-  clean_names() %>% 
-  mutate(exp_per_visit = expenditure / visits,
-         exp_per_visit_pct_change = (exp_per_visit - lag(exp_per_visit)) / lag(exp_per_visit) * 100,
-         visit_pct_change = (visits - lag(visits)) / lag(visits) * 100,
-         exp_pct_change = (expenditure - lag(expenditure)) / lag(expenditure) * 100,
-  
-         visits_change_label = case_when(visits > lag(visits) ~ "Increased",
[…]

### 2023-06-19 visit_scotland_analysis.Rmd
Updated README.md / Added Summary Stat Working To Analysis

@@
 ```{r}
+regional_data_joined %>% 
+  group_by(local_authority) %>% 
+  summarise(mean_visits = mean(visits)) %>% 
+  arrange(desc(mean_visits))
+```
+
+```{r}
 
@@
 #### Expenditure by Region
+
+```{r}
+regional_data_joined %>% 
+  group_by(local_authority) %>% 
+  summarise(mean_expenditure = mean(expenditure)) %>% 
+  arrange(desc(mean_expenditure))
+```
 
@@
   ggplot(aes(fill = mean_visits)) + 
-  geom_sf(colour = "grey90", size = 0.1) +
+  geom_sf(colour = "grey90", size = 0.5) +
   labs(

### 2023-06-19 scripts/cleaning_script.R
Minor Formatting Updates

@@ -14,11 +14,12 @@ local_authority_codes <- read_csv("data/raw_data/local_authority_codes.csv")
 
 international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv")
 
+tourism_businesses <- read_csv(here("data/raw_data/tourism-businesses-in-scotland.csv")) %>% 
+  clean_names()
+
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
 
-tourism_businesses <- read_csv(here("data/raw_data/tourism-businesses-in-scotland.csv")) %>% clean_names()
-
-# Domestic Tourism Data ------------------------------------------------------------
+# National Domestic Tourism Data ------------------------------------------------------------
 
 domestic_annual_clean <- read_csv("data/raw_data/gbts_scotland_annual.csv") %>% 
   mutate(dom_int = "Domestic", .after = year)

### 2023-06-20 visit_scotland_analysis.Rmd
Minor Formatting Updates
Labelling Consistency Updates on Visualisations

@@
 
-### Over Time / Spend
+### Over Time / Expenditure
 
@@
 
-#### Spend Per Visit
+#### Expenditure Per Visit
 
-##### Mean Spend Per Visit Plot
+##### Mean Expenditure Per Visit Plot
 
@@
 
-##### Spend Per Visit by Country of Residence
+##### Expenditure Per Visit by Country of Residence
 
@@
 
-##### Linear Model: Predict Spend by Visits
+##### Linear Model: Predict Expenditure by Visits
 
@@
 
-### Total Spend by Country of Residence
+### Total Expenditure by Country of Residence
 
@@
     x = "Country",
-    y = "Total Spend (Million GBP)",
-    title = "International Tourism: Total Spend (2002-2009)",
+    y = "Total Expenditure (Million GBP)",
+    title = "International Tourism: Total Expenditure (2002-2009)",
     subtitle = "Top 20 (Holiday Only)") +
@@
 
-### Spend per Visit by Country of Residence
+### Expenditure per Visit by Country of Residence
 
@@
     x = "Country",
-    y = "Total Spend (Million GBP) / Visit (Thousands)",
-    title = "International Tourism: Total Spend per Visit (2002-2009)",
+    y = "Total Expenditure (Million GBP) / Total Visits (Thousands)",
+    title = "International Tourism: Total Expenditure per Visit (2002-2009)",
     subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +
@@
     x = "Visits (Thousands)",
-    y = "Total Spend (Million GBP) / Visit (Thousands)",
-    title = "International Tourism: Visits vs. Spend Per Visit (2002-2009)",
+    y = "Total Expenditure (Million GBP) / Total Visits (Thousands)",
+    title = "International Tourism: Visits vs. Expenditure Per Visit (2002-2009)",
     subtitle = "Countries w/ Over 500 Thousand Total Visits (Holiday Only)") +

### 2023-06-20 scripts/cleaning_script.R
Tidying of Cleaning Script

@@ -14,7 +14,7 @@ local_authority_codes <- read_csv("data/raw_data/local_authority_codes.csv")
 
 international_visits <- read_csv("data/raw_data/international-passenger-survey-scotland-2019.csv")
 
-tourism_businesses <- read_csv(here("data/raw_data/tourism-businesses-in-scotland.csv")) %>% 
+tourism_businesses <- read_csv("data/raw_data/tourism-businesses-in-scotland.csv") %>% 
   clean_names()
 
 local_authority_geo <- st_read(dsn = "data/geo_data/", layer = "pub_las")
@@ -74,7 +74,8 @@ dom_int_summary <- bind_rows(domestic_annual_clean, international_visits_annual_
 
 tourism_businesses_clean <- tourism_businesses %>%
   clean_names() %>% 
-  select(-x7)
+  select(-x7) %>% 
+  filter(local_authority != "- Select -")
 
 # Write Clean Data To .CSV -----------------------------------------------------------
 

### 2023-06-21 visit_scotland_analysis.Rmd
Minor Plot Labelling Updates

@@
        title = "Annual Visits",
-       subtitle = "Domestic & International Overnight Vistors",
+       subtitle = "Domestic & International Overnight Vistors (2009-2019)",
        colour = "") +
@@
        title = "Annual Expenditure",
-       subtitle = "Domestic & International Overnight Vistors",
+       subtitle = "Domestic & International Overnight Vistors (2009-2019)",
        colour = "") +
@@
   mutate(exp_per_visit = spend / visits,
-         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  group_by(spring_summer) %>% 
+         spring_summer = if_else(quarter %in% c("Quarter 2", "Quarter 3"), "Yes", "No")) %>%  
+  group_by(spring_summer) %>% 
   summarise(mean_visits = mean(visits),

### 2023-07-05 visit_scotland_analysis.Rmd
Updates To Geospatial Aesthetics & README.md Screenshots

@@
   ggplot(aes(fill = mean_visits)) + 
-  geom_sf(colour = "grey90", size = 0.1) +
+  geom_sf(colour = "white", linewidth = 0.04) +
   labs(
@@
   ggplot(aes(fill = mean_exp)) + 
-  geom_sf(colour = "grey90", size = 0.1) +
+  geom_sf(colour = "white", linewidth = 0.04) +
   labs(
@@
   ggplot(aes(fill = mean_nights_per_visit)) + 
-  geom_sf(colour = "grey90", size = 0.1) +
+  geom_sf(colour = "white", linewidth = 0.04) +
   labs(
@@
   ggplot(aes(fill = mean_visits)) + 
-  geom_sf(colour = "grey90", size = 0.5) +
+  geom_sf(colour = "white", linewidth = 0.04) +
   labs(
